### 2014-09-19 paper/paper1.tex
paper

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\begin{document}

%
%
\title{XXXXX}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

\keywords{..}
\end{abstract}
%

\section{Introduction}

\section{Idea}

\begin{itemize}
	\item sind alle constraints abgedeckt?
	\item kann man alle constraints in SPARQL definieren?
	\item sind alle constraints mit Logik ausdrückbar?
	\item vollständig mit Reasoning | OW
	\item vollständig ohne Reasoning | CW
	\item es gibt keinen query rewriting mechanismus für OWL 2, nur für OWL-QL
	\item constraints in einer anderen constraint language definieren wenn constraints nicht in OWL beschrieben werden können
	\item durch reasoning entstehen Probleme, auf die man nicht gekommen wäre --> sofort nachvollziehbar
	\item zeigen, dass OWL-QL und constraint language einer konkreten Domäne zusammen vollständig sind
	\item System entwickeln, das effizient ist / Experimente
\end{itemize}

-----

Nehmen wir nun an, dass dein Framework welches entsprechende SPARQL Queries generiert diese auf einem SPARQL Endpoint evaluiert der zu der vorliegenden Ontologie bzw. des darin verwendeten OWL 2 Profils das entsprechende Entailment Regime realisiert, wären die zurückgegebenen Resultsets vollständig. Wie das Entailment Regime im Endpoint realisiert ist, also durch Query Rewriting oder durch Vervollständigung der ABox, ist dabei irrelevant.

Wie allerdings bspw. in 
\url{https://www.uni-ulm.de/fileadmin/website_uni_ulm/iui.inst.090/Lehre/WS_2011-2012/SemWebGrundlagen/LectureNotes.pdf}
auf Seite 51 veranschaulicht, ist die Komplexität des Reasoning abhängig von der zugrunde gelegten Sprache und kann daher nur in bestimmten Fällen effizient durchgeführt werden. Wie in unserem letzten Paper beschrieben zielt unter anderem die Definition von DL-Lite gerade darauf ab Reasoning Aufgaben und Query Answering effizient zu ermöglichen und ist Grundlage des OWL 2 QL Profils. Nun ist allgemein bekannt, dass die logische Konsistenz für diese Art von Sprachen effizient geprüft werden kann.

Allerding wäre wie bspw. in 
\url{http://www.aifb.kit.edu/images/d/d2/2005_925_Haase_Consistent_Evol_1.pdf} beschrieben auch eine sogenannte 'User-defined Consistency' denkbar. Genau an dieser Stelle könnten wir ansetzen.

\section{research questions}

\begin{itemize}
	\item for which RDF validation requirement the expressivity of DL-LiteA respectively OWL 2 QL is sufficient?
	\item for which RDF validation requirement additional constraint languages are needed?
	\item which constraint languages are suitable to express remaining requirements?
	\item what are the effects of these constraints regarding complexity?
\end{itemize}

\section{Related Work}

\section{Evaluation}

evaluation using practical data set

\section{Conclusion and Future Work}

\bibliography{literatur}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2014-09-19 paper/paper2.tex
paper

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\begin{document}

%
%
\title{Constraint Validation with OWL 2 | Closed World Semantics | With and Without Reasoning}
%
\titlerunning{Constraint Validation with OWL 2}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
OWL (and RDFS) semantics (and syntax) can be used to specify constraints.

\keywords{..}
\end{abstract}
%

\section{Introduction}

\section{OWL as Constraint Validation Language}

\subsection{Compact, Human-Readable Syntax}

1 (2) example(s)

\begin{enumerate}
	\item SPARQL
	\item SPIN (Turtle syntax)
	\item OWL 2 (Turtle syntax)
	\item OWL 2 (Manchester Syntax)
\end{enumerate}

\textbf{cardinality restrictions}

for the simple cases the sytax in compact form and manchester are not that different. 
As well as showing that the RDF versions are quite close as well.

In Shex Compact (corrections welcome),

\begin{ex}
<WebServicePersonShape> {
  rdf:type foad:Person ,
  foaf:name xsd:string ,
  foo:email xsd:string ,
  foo:phone xsd:string *
}
\end{ex}

In ShEx RDF
\begin{ex}
<WebServicePersonShape> a rs:ResourceShape ;
     rs:property  [ rs:name                "one name" ;
                    rs:occurs              rs:Exactly-one .  ;
                    rs:propertyDefinition  foaf:name ;
                    rs:valueShape          foaf:Person
                   ],
                   [ rs:name                "one e mail" ;
                    rs:occurs              rs:Exactly-one ;
                    rs:propertyDefinition  foo:email ;
                    rs:valueShape          foaf:Person
                   ] ,
                   [ rs:name                "some number of phone numbers" ;
                    rs:occurs              rs:Zero-or-many ;
                    rs:propertyDefinition  foo:phone ;
                    rs:valueShape          foaf:Person
                   ] ;
\end{ex}

In spin turtle

\begin{ex}
foaf:person a owl:Class;
  spin:constraint [ rdfs:label "one name" ;
                    a spl:Attribute ;
                    spl:predicate foaf:name ;
                    spl:count 1 ] ,
                  [ rdfs:label "one e-mail" ;
                    a spl:Attribute ;
                    spl:predicate foo:email ;
                    spl:count 1 ] ,
                  [ rdfs:label "some number of phone numbers"
                    a spl:Attribute ;
                    spl:predicate foo:phone ;
                    spl:minCount 0 ] .
\end{ex}

--> As given it looks horrible, but with a compact syntax on top

In Closed world owl rdf turtle serialisation

\begin{ex}
foaf:person a owl:Class;
  rdfs:subClassOf [ a       owl:Restriction ;
                    owl:cardinality "1"^^xsd:nonNegativeInteger ;
                    owl:onProperty foaf:name ;
                    rdfs:label "one name"
                  ] ,
                  [ a       owl:Restriction ;
                    owl:cardinality "1"^^xsd:nonNegativeInteger ;
                    owl:onProperty foo:email ;
                    rdfs:label "one email"
                  ] ,
                  [ a       owl:Restriction ;
                    owl:minCardinality "0"^^xsd:nonNegativeInteger ;
                    owl:onProperty foo:phone ;
                    rdfs:label "some number of phone numbers"
                  ] ,
\end{ex}

Some Manchester syntax (again corrections welcome)

\begin{ex}
Class: foaf:person
   foaf:name exactly 1
   foo:email exactly 1
   foo:phone min 0
\end{ex}

which existing technology should be used as guide. 
As well as showing what the technologies in the field can do already.

\textbf{syntactically well-formed email addresses}

\tb{example}

Yes, your specific example can be 
nicely represented in a very compact textual form. But your example only 
talks about cardinality, and there is obviously much more that people 
want to specify when they publish data models. For example you may want 
to say that the values of foo:email are syntactically well-formed email 
addresses. Simple languages quickly reach limits and then need to be 
overloaded with all kinds of escape mechanisms.

RDF is designed to be 
extensible - anyone can add their own classes and properties to 
represent any kind of extra information. Therefore a model that talks 
about other data models should also be represented in RDF, and that's 
where Shapes come into the picture. For certain common shapes (such as 
cardinality) a short-hand syntax could be added, but still the 
underlying semantics need to be more flexible.

\textbf{JSON-LD.}

example:

\begin{ex}
{
     "@context" : "http://w3.org/2014/shapes/context",
     "@id" : "ex:Person",
     "constraint" : {
         "type" : "shapes:Property",
         "property" : "ex:firstName",
         "occurs" : "shapes:Exactly-one",
         "valueType" : "xsd:string"
     }
}

\end{ex}

benefits:

- understandable by anyone who does some coding, without being a "semantic web engineer."

\textbf{Why compact human-readable syntax?}
don't think RDF, don't know RDF, they don't want to know RDF.
They don't think open world or closed world, etc.

Writing validation rules in RDF would be simpler than writing them in SPARQL,
but still much more tedious than having a concise, compact syntax for
expressing them.

\textbf{requirements on compact human-readable syntax.}

- understandable by anyone who does some coding, without being a "semantic web engineer."

- Now the question is: who creates this and how? And do they have to be fully versed in RDF?

\textbf{structure of syntax.}
The structure itself should guide novices to make good RDF-compatible decisions.

\textbf{expressing constraints in OWL enables thinking in RDF. | syntax using the same paradigm and semantics of RDF [important!]}

We need a syntax that is related to RDF, uses the same paradigm and semantics.

I've seen RDF/XML and, to a lesser extent, JSON-LD act as gateways to 
RDF. (I almost wanted to say: gateway drugs.) The down side of that is 
that users tend not to learn to think in terms of key RDF concepts like 
graphs, inferencing, and the meaning of class membership in RDF. So it 
does help that there are known serializations, but those known 
serializations can hide the ways that RDF semantics differ from our 
previous ways of thinking about data. Therefore people tend to create 
perfectly good XML or JSON data that isn't RDF at heart.

My concern is that we had this confusion before: When RDF and OWL were standardized, they came with RDF/XML syntax only, and people thought this semantic web is just another kind of XML. But a complicating kind of XML, where the idea of graphs was hidden behind rdf:ID and rdf:about attributes.

From the data model perspective, RDF was never a kind of XML. It can be serialized as XML, but it has a different data model. This difference was, perhaps, obvious to the standard committee and they never thought anyone would be confused or that this confusion would be an issue.

In reality, this was, however,  a big issue. It was very difficult for other people to understand what RDF was without a lot of education that had to change the assumptions they quickly made after first getting to know about RDF. First impressions are hard to change. Things became easier after Turtle became better known as the way to serialize and RDF/XML faded into background as just one (lesser used) serialization.

\subsection{Readability in the face of complexity and internationalization of human friendly syntaxes}

\textbf{use of templates for better readability and management of complexity}

complexity needs to be managed not ignored.

example in a number of syntaxes.

In ShEX Compact

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email xsd:string ,
  foo:phone xsd:string *
}
\end{ex}

In ShEx RDF

\begin{ex}
<WebServicePersonShape> a rs:ResourceShape ;
   rs:property  [ rs:occurs              rs:Exactly-one .  ;
                  rs:propertyDefinition  foaf:name ;
                  rs:valueShape          foaf:Person ],
                 [ rs:occurs              rs:Exactly-one ;
                  rs:propertyDefinition  foo:email ;
                  rs:valueShape          foaf:Person ] ,
                 [ rs:occurs              rs:Zero-or-many ;
                  rs:propertyDefinition  foo:phone ;
                  rs:valueShape          foaf:Person ] .
\end{ex}

In SPIN turtle

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

Now we change the requirements very slightly. Instead of any string being acceptable as e-mail we need to ensure
it is actually a valid e-mail for an employee in our organisation.

How would you determine what is a valid e-mail for an employee in a organisation?
The first approach is to say that it has to match a specific regex. e.g. for the university I went to any e-mail
address of an employee needs to match the regex \begin{verbatim}“.+@pl.hanze.nl^”\end{verbatim}.

Let's try that in ShEx compact shall we.

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email IRI %sparql{ ?s foo:email ?mbox . FILTER (REGEX(str(?mbox), “.+@pl.hanze.nl^”) %}
  foo:phone xsd:string *
}
\end{ex}

And in spin turtle

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ] ,
                [ sp:text “ASK{?s foo:email ?mbox . FILTER (!(REGEX(str(?mbox), “.+@pl.hanze.nl^”)) }"
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

This can be simplified again with a template library e.g. similar to of the ones given at [1].

\begin{ex}
our-company:employee-email 
      a       spin:Template ;
      rdfs:comment "This template check a IRI to be a valid employee e-mail property ?arg1."@en ;
      rdfs:label "syntax check in all instances:  valid employee email"@en ;
      spin:body
              [ sp:text """CONSTRUCT {
                 _:b0 a spin:ConstraintViolation .
                 _:b0 spin:violationRoot ?s .
                 _:b0 spin:violationPath ?arg1 .
                }
                WHERE {
                 ?arg1 foo:email ?mbox .
                 FILTER (!(REGEX(str(?mbox), “.+@pl.hanze.nl^”))
                }""" ;
\end{ex}

So now the spin turtle becomes

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ;
		  a our-company:employee-email] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

Which is more likely to be readable to the “business” users.

The second advantage of this kind of approach is that these templates are maintainable independently from the rules themselves.

This becomes even more the case when the validation starts to be more complicated.
Few companies have a clean separation between e-mails addresses for employees and mailing lists.
However, most do have a LDAP or equivalent system. Assuming Squirrel RDF for LDAP[2] is still working
a system can adapt that as an information source.

Shex now turns into this.

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email IRI %sparql{ ?s foo:email ?mbox . SERVICE<ourcompanyLdap>{ ?employee foaf:mbox ?mbox ; a :Employee }) %}
  foo:phone xsd:string *
}
\end{ex}

While the SPIN solution stays like this.

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ;
		  a our-company:employee-email] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

The SPIN solution can be made more compact if it had more predicates e.g.

\begin{ex}
foaf:person a owl:Class;
shape:hasOne  [ spl:predicate foaf:name  ] ,
	      [ a our-company:employee-email ] .
shape:some    [ spl:predicate foo:phone ] .
\end{ex}

Compare this to the compact ShEx form? Is the SPIN one that bad?

\subsection{define vocabulary terms and constraints with the same syntax}
If you want to properly publish a "schema" then 
you also need a way to define the properties and classes that are used, 
together with their rdfs:labels, rdfs:comments, relationships etc. These 
are attached to the properties globally, and already exist in triple 
format. Developers would end up using a Turtle/JSON-LD file for one part 
of their schema, and then a custom syntax just for the constraints?

\section{Class-Based Validation}

Constraints can be associated with instances of RDFS/OWL types.  
I view the ability to associate constraints with instances of types as the most important aspect of a constraint system.

\tb{how is it done using our approach}

\subsection{modularization of constraints / class-based validation vs. shapes-based validation}

constraints can be hosted by a "Shape" object or to an OWL class.

\textbf{class-based validation}

If we want to be based on RDF, then we should honor its basic principles. One of those principles is that of self-describing data, where applications can look up the definition of a resource by resolving URIs. For example, if a resource declares an rdf:type, then an application should be able to look up the definition of the class, including its semantic declarations and constraints. This should be the default assumption: someone creates an ontology and when he publishes it on the web then anyone who wants to reuse that ontology should honor the same constraints.

Having said this, applications may overload the default behavior. In TopBraid we do this by first looking at local files for the same URI, and preferring those over the files from the web. This also makes it possible to refer to graphs that do not even exist on the web.

\textbf{shapes-based validation}

When resources do not even have to have an rdf:type - how is this going to be
self-describing data? What is the entry point into the validation?"

- It is self-describing because the Shape is either linked to the service
description or the instance document.

- The entry point is the entire RDF document (aka graph) just like in
SPARQL.  There is not necessarily a special node in the graph. You use a
general graph pattern to either find a subgraph that must exist (an
assertion), or to find a subgraph that must not exist (a constraint
violation).

This is motivated by Linked Data API considerations. Here
one deals with REST services. For example, when creating new resources,
one POSTs an RDF document to some URL. We want to describe the API
contract for the service. The service is described by a Service
Description resource. The Service Description resource refers to the Shape
accepted by the POST request. Shape may require that the request contains
a node with an rdf:type property. However, the Shape may apply to several
different rdf:types. The Shape is therefore attached to the service, not
each type. After the resource is POSTed, the service may added new
triples, so the Shape of the created resource is different than the Shape
of the POST request. The created resource may contain a link to its Shape.
A service that lets you query across a set of resources may also link to a
set of Shapes that define the data available for querying. This metadata
both tells you what properties are available and may let you define more
efficient queries.

The above use cases are orthogonal to use cases where an RDF class defines
constraints that must be universally obeyed, independent of the context,
i.e. a bicycle must have two wheels.

We have seen many more examples of the
latter than the former, and I believe the structure of existing ontology
languages suggests that it should be possible to "attach" constraints to
classes. I personally believe your use case is the exception, not the
rule, but of course I would like to see a generic solution that covers
all use cases so that the standardization process succeeds.

% -

Well if you only consider constraints for objects of properties, 
then it may turn out that constraints associated with an RDF class
are in the minority.  Of course, I strongly feel that constraints for objects
of properties is not a central aspect of RDF validation.

\subsection{Pros}

In our experience, having an rdf:type is the norm, and typeless resources are 
the exception. I don't think it is a good idea to base the design of 
such an important aspect on the exception cases. Attaching 
the semantics to classes gives you a natural way of encapsulation, 
inheritance and allows us to reuse all existing ontologies in an 
incremental way, rather than coming up with a parallel world of 
free-floating shapes.
- Object-orientation is mainstream.
- (simple and consistent) "object-oriented" design used by all other ontology languages.
In our experience, using rdf:type triples and classes is a more intuitive mechanism, and it 
already exists, is consistent with OWL etc.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

Yes: RDF is all about graphs, but does 
this mean that a constraint language may not exploit certain triples 
from those graphs and give them special meaning?
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

Another analogy is XML, where every XML element also has a name. This is 
comparable to its rdf:type.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

If we are talking about Linked Data and want to stay
aligned with the way that ontologies are currently being built, then
relating constraints to classes remains a requirement.

\subsection{Cons}
An RDF document is a set of triples (statements). The triples do not 
necessarily have to look like they came from an object (in the OO sense), 
i.e. that there is one distinguished root node (this, self) that has some 
type (class) attribute, and other triples (properties) that have the root 
node as their subject, and so on recursively. 
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

If you think of an RDF document as a graph, then there should be no special 
significance to a node that happens to have a type attribute. We should be 
able to state constraints on the graph in the absence of type triples. 
This is very consistent with SPARQL. SPARQL includes a graph pattern 
matching language. SPARQL queries are not associated with any specific 
type, so why should constraints be?
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

However, even if the RDF document was the representation of some OO-like 
object that had a root node and some type (class) attribute, its shape 
could vary depending on the context. For example, when you create a 
resource using POST, certain triples will be absent, e.g. creation date, 
and if present they may be ignored or the server may fail the request. 
When you GET that resource you will normally see other triples that the 
server added, e.g. creation date, and these will occur exactly once. 
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

OSLC lets you associate shapes with operations. Resource instances may 
link to shape resources that describe the instance. There is no need to 
base the association between resources and constraints using an RDF type. 
A shape could apply to several types or to no types.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

\section{Inferencing as a pre/post validation step | Reasoning and Constraint Checking}

Both should be possible:

\begin{itemize}
	\item Constraint Checking with Reasoning
	\item Constraint Checking without Reasoning
\end{itemize}

\subsection{our approach}

Existential Quantification on Object Properties

constraint (formal syntax):
\begin{ex}

\end{ex}

constraint (Manchester syntax):
\begin{ex}

\end{ex}

constraint (functional-style syntax):
\begin{ex}
SubClassOf( ObjectSomeValuesFrom( :hasDog owl:Thing ) :DogOwner ) 
\end{ex}

constraint (turtle syntax):
\begin{ex}
    _:x 
        a owl:Restriction ;
        owl:onProperty :hasDog ;
        owl:someValuesFrom owl:Thing ;
        rdfs:subClassOf :DogOwner .
\end{ex}

data (Turtle syntax):
\begin{ex}
    :Peter 
        a owl:Thing , owl2spin:ToInfer ; 
        :hasDog :Brian . 	
    :Brian
        a owl:Thing .
\end{ex}

inferred triples (Turtle syntax):
\begin{ex}
:Peter a :DogOwner .
\end{ex}

\subsection{Constraint Checking with Reasoning}

Constraint validation does not appear to be part of the services provided by
OWL.  This has lead to claims that OWL cannot be used for constraint
validation.  However inference, which is the core service provided by OWL,
and constraint validation are indeed very closely related.

Inference is the process of determining what follows from what has been
stated.  Inference ranges from simple (students are people, John is a
student, therefore John is a person) to the very complex.  Inference can
also recognize impossibilities (students are people, John is a student, John
is not a person, therefore there is a contradiction).  In the presence of
complete information, nothing new can be inferred, so inference only checks
for impossibilities, i.e., constraint violations.  So the way do constraints
in OWL is to first set up complete information, and then just perform
inference [this is related work].

For example, with the concept axiom

\begin{ex}
  ex:Person <= =1 foaf:name & all foaf:name xsd:string &
               =1 foaf:phone & all foaf:phone xsd:string &
               =2 ex:child
\end{ex}

and in the presence of (locally) complete information, such as

\begin{ex}
  <John> in ex:Person .
  <John> foaf:name "John"^^xsd:string .
  <John> foaf:phone "+19085551212"^^xsd:string .
  <John> ex:child <Bill> .
  <John> ex:child <William> .
  <John> in <=1 foaf:name .
  <John> in <=1 foaf:phone .
  <John> in all child {<Bill>, <William>, <Susan>} .
  <Bill> /= <William> .
  <Bill> /= <Susan> .
  <Susan> /= <John> .
\end{ex}

determining whether <John> belongs to ex:Person is just constraint validation.

Setting up complete information is just what was done above.  In a model
there is complete information, so considering an RDF graph (plus
consequences) as a model turns OWL inference into constraint validation.
Of course, this doesn't mean that you have to implement OWL inference in a
model the same way that you need to with incomplete information.  In fact,
as above, constraint validation can be implemented as SPARQL queries.

Conclusion

In fact the main difference between recognition and constraint checking is
that the former either has no axioms or only uses axioms defining names that
do not occur in the RDF graph whereas constraint checking uses axioms that
relate concepts appearing in the RDF graph to descriptions.

So OWL can indeed be used for both the syntax and semantics of constraint
checking and closed-world recognition in RDF, and most or all of it can be
implemented using a translation to SPARQL queries.

-----

\begin{enumerate}
	\item inference --> complete model
	\item constraint checking
\end{enumerate}

-----

Mentioning the use of inferencing as a pre/post validation step option is perfectly fine, enforcing it is a completely different thing.

Well it's not as simple as just mentioning that inferencing is a pre/post 
validation step option, depending on how your validation process is defined. 
To make validation play well with inference you may have to be able to handle 
infinite sets and multiple models on one side and too-central-to-turn-off 
inferences on the other.

% -

\textbf{use structural information for inferencing}

- use structural information to produce new output (e.g. XML trees or other RDF triples) (see ShEx paper)

\textbf{rules}

- Another example is spin:rule, which is in our experience 
tremendously useful for defining mappings between ontologies, and to
calculate the ex:area of a ex:Rectangle from ex:width and ex:height.
Once we have a mechanism to attach SPARQL and templates to classes for
constraint checking, we could use exactly the same mechanism to define
such production rules.

% -

\textbf{sub-class super-class inferencing}

Constraint definitions attached to a superclass (assuming
Shape=class) need to also apply to instances of a subclass.

\subsection{Constraint Validation Without Reasoning}

\section{Context-Sensitive Constraint Validation}

main assertions:
\begin{itemize}
	\item Reasoning and Closed World Assumption
	\item constraints depend on the context
\end{itemize}

But without reasoning things can work very well as well.

reasoning would either hide the error

There is an underlying practical problem, which we face daily in the management of the LOV repository.
Again, it's not a minor point that RDF uses URIs for classes and properties. If you find a class or property URI somewhere in data (e.g., DBpedia) how do you figure the semantics of this URI, IOW how do you find the document(s) you are speaking about which define it, and which ones will you abide by, to figure in practice the closure of the description of this URI? 
Look at the result of this query  http://bit.ly/UPGA25  ran on current LOV database of 450 vocabularies/ontologies. It yields all elements related to foaf:Person in various namespaces (and so many documents). Somehow each of those 300+ assertions is refining the semantics of foaf:Person. If you ignore the 25 ones defined by the foaf: namespace itself, you are lefy with more than twenty different namespaces/vocabularies/documents to explore, and select or not to figure the closure.

Of course, looking only at the FOAF vocabulary using a HTTP GET on foaf:Person, you will not access and even be aware of all this extra semantics, and you can ignore it, apart of those which FOAF itself reuses.

This is an extreme case maybe, but it illustrates what the practical problem will be, when using a URI, to first find out to which semantics you abide by before passing it to reasoners or constraint checkers. One could imagine something like a content negotiation on the URI where you pass in parameters the type of description you want for this URI (give me SPIN, OWL, Shapes ...). But given the messy way content negotiation is already implemented after httpRange14 resolution (based also on our LOV experience), I'm very skeptical about such a solution in practice. Moreover, different parties will use different documents of which the original URI owner does not control, is not aware of, let alone agrees with.

My concern is to see a door wide open to more balkanization of the Semantic Web, each tribe abiding by its own, not necessarily public, interpretation of shared vocabularies.

So if you use RDFS and OWL, and include a lot of constraints, then the
terms are not very reusable because they carry a lot of baggage in the
form of inferences which may not make sense in your application.

Note that I am describing the state of the practice. Many ontologies in 
fact do contain a lot of inferences and this makes them less reusable. 
This is true even in absence of constraints since W3C OWL doesn't 
officially handle constraints, just inference rules.

The point I was trying to make is that applications often need to impose 
additional constraints on terms and that these constraints often depend on 
the context.

Let's refocus the discussion on how an application designer would reuse an 
externally published OWL ontology and impose additional constraints. Let's 
assume OWL IC semantics. What would the application designer provide to 
describe a REST API that required exactly one dcterms:title triple in the 
request body on POST?

% -----

\subsection{entailment regimes}

ShEx and Resource Shapes work on an RDF graph.  This does not mean that they 
can be used in combination with a reasoner, even an RDF reasoner.  SPARQL has 
entailment regimes, which specifies how SPARQL is supposed to work with reasoning.

Consider, for example, that there are infinitely many RDF consequences of a 
finite RDF graph.  How do I run ShEx and Resource Shapes on an infinite graph?

Consider, for example, that the OWL consequences of a finite RDF graph are 
generally not representable as an RDF graph.  How do I combine ShEx or 
Resource Shapes with OWL?

\textbf{support of inferences from ontologies}
It may be that there are many ontologies that support a lot of inferences.
However, there are lots of ontologies that are small and do not support a
lot of inferences.  RDFS and OWL can be used both ways.

Further, why should an ontology that supports many inferences be
undesirable, even if it is less reusable?  I don't think that you can argue
that reusability is a good in and of itself.  For example, the ontology
containing only the axiom stating that owl:Thing is a subclass of owl:Thing
is maximally reusable, but not very useful.

\section{Comparison of Validation/Constraint Languages | Why OWL 2 and SPARQL for RDF Validation?}

\textbf{dependencies between validation languages}

Here is a diagram draft illustrating the dependencies among various 
Semantic Web languages, as I see them:

     https://twitter.com/HolgerKnublauch/statuses/494648159931346944

The stacking of boxes on top of each other means "uses features of". 
Please don't get caught up in details. The points that I am trying to 
make are:

- There can be multiple "schema" languages for the same RDF models

- Different languages have different design goals (e.g. OWL was mainly 
created for classification tasks)

- All these languages can live alongside with each other without 
breaking each others interpretations, for example via separate import 
mechanisms (owl:imports, spin:imports, ic:imports). A SPIN model can 
ignore OWL constructs, but SPARQL queries can also be executed on top of 
graphs that have OWL inferencing activated. Likewise, OWL models can 
ignore spin:constraint definitions.

To me one of the important things is to ensure that classes, properties 
and instances can be reused. The concept of "Classes" is quite basic, 
established and successful, and is therefore a good foundation for 
Shapes too.

And yes, I am fully aware that there are other languages that did not 
make it into this diagram. I just wanted to focus on the comparison 
between OWL and Shapes+SPIN and make clear that this is not an either-or 
discussion. There is plenty of space for both approaches, and indeed 
both "communities" can benefit from each other when the Semantic Web 
grows as a whole.

\textbf{Why OWL & SPARQL for RDF validation?}

\begin{itemize}
	\item OWL & SPARQL are sufficient for validation in a CWA
	\item Normally, the RDF has already an OWL / RDFS. Thus, part of those declarations will be defined anyway
	\item In most cases reusing existing OWL schemas for validation is enough
	\item What we need in the end is tools that translate OWL to SPARQL - or to something intermediate like ShEx or SPIN
	\item language that many people already know
	\item in practice that most people out there make use of RDFS and OWL constructs to tell other people and applications about how valid instances should be created.Whether this is good or bad is another question, but that's the reality.
	\item OWL semantics:
Most people don't care about open world semantics, but of course nobody would admit that because it's against the specs and thousands of academic papers.
	\item could be interpreted either with the open world assumption to support open world reasoning, and (exactly the same piece) interpreted in closed world applications as a constraint for interfaces or a validation rule
\end{itemize}

\textbf{difference between a declarative validation / constraint language (e.g. OWL 2, ShEx) and a more general purpose validation / constraint language (e.g. SPARQL)}

\textbf{Why declarative validation / constraint language?}

a human readable syntax is vastly preferable to an RDF based syntax

\textbf{Why general purpose validation / constraint language?}

- maximum expressivity
	- SPARQL is very expressive, so most typical constraints can be expressed
	- need to express more complicated constraints, and SPARQL is the best available language to represent those

\textbf{Why NOT general purpose validation / constraint language?}

too low-level:
SPARQL is too low-level. If you look at a SPARQL query, you'd have a hard time figuring out what constraint it is checking.

\textbf{Why OWL / OWL 2 for RDF validation?}

\textbf{Why NOT OWL / OWL 2 for RDF validation?}

The problem with OWL is the different semantics so people have to rewrite it in another languages such as SPIN / ShEx / SPARQL

http://composing-the-semantic-web.blogspot.com.au/2010/04/where-owl-fails.html

intended for
(1) semantic description
(2) reasoning: infer new triples from a given set of triples

not intended for
(1) validation
(2) describe a database structure

Why not use OWL to describe database structures? (example)

it is hard to read an OWL ontology to understand the structure of a database.

ShEx:

\begin{ex}
A {
  (ex:samepred1 @B | ex:samepred1 @E) #either referencing B or E
}
C {
  ex:samepred1 @D
}
\end{ex}

OWL:

\begin{ex}
Class A -> ex:samepred1 -> Class B
Class C -> ex:samepred1 -> Class D
A <= all ex:samepred1 Extra
C <= all ex:samePred1 D
Class B -> rdfs:subClassOf -> Class Extra
Class E -> rdfs:subClassOf -> Class Extra
\end{ex}

Here have an extra class 'Extra' for which it is not clear whether is created for making the ontology work or is an actual Concept in my database.

OWL has disjunction, so you can say
A <= all ex:samepred1 (B or E)
which is even better than the ShEx version you give.

(3) to be used as Schema language for validation
(4) further reasons:  conclusion of this paper (http://arxiv.org/pdf/1404.1270v1.pdf)
(5) Another thing you can not do in OWL is to define the following:

\begin{ex}
Type A -> ex:samepred1 -> Type B
Type C -> ex:samepred1 -> Type D
\end{ex}

If you would define this in OWL you will also get, because OWL is property oriented and a property can only define a range and domain

\begin{ex}
Type A -> ex:samepred1 -> Type D
Type C -> ex:samepred1 -> Type B
\end{ex}

Which is something we do not want.

Why do you say that?  OWL includes many constructs that are local.  Here you
can use allValuesFrom, as in

\begin{ex}
A <= all ex:samepred1 B
C <= all ex:samePred1 D
\end{ex}

\begin{itemize}
	\item 
	Clark & Parsia had previously proposed the ICV semantics for OWL, but this was not submitted to W3C.
	\item
	Ambiguousness when OWL would be used assuming both OWA (for inferencing) and CWA (for constraint validation) (see section XXXXX).
It would be somewhat confusing to have two completely different semantics for OWL.
	\item
	OWL cannot represent all possible use cases
\end{itemize}

(6) modeling goals / orientation

SHEX is oriented on Shapes and Shape Properties (Property per shape), 
whereas OWL is oriented on (Restriction) Classes and Properties.
Orientation on (Restriction) Classes and Properties is a logic and the best thing to do when working in the world of reasoning.

However if we look from user point of view, which would like to understand the structure of database or interface of a service then an orientation on Shape and Shape Properties is better. This is what a user needs when he wants to write some queries for a database as noted earlier on by me.

\textbf{OWL vs. ShEx}

OWL is very good at semantic level / Shape Expressions are more suited for the syntactic level or data integration level

classes are semantic / shapes are syntactic

OWL: inferencing

ShEx: looks at the shape of the RDF graph

\textbf{Why SPIN?}

combines the flexibility of SPARQL with the simple declarative syntax of RDF triples

SPIN is self-describing

is extensible to any constraint

grows with the evolution and adoption of SPARQL

\section{Validation using Closed World vs. Open World Semantics | OWL Closed World + SPARQL for RDF Validation | Underlying Semantics / Assumptions: Closed World Assumption and Unique Name Assumption}

Underlying Assumptions: Closed World Assumption and Unique Name Assumption

OWL descriptions and the OWL semantics provide the necessary framework for
both validating constraints and providing recognition facilities.
Why then are there claims that
OWL is inadequate for these purposes?  I do not know why, but there are
several aspects of OWL that might not be consonant with constraints and the
kind of recognition that might be desired.  However, it turns out that both
OWL syntax and semantics are arguably the right solution for RDF constraint
checking and closed-world recognition.

Closed-World Recognition / class assertions

Determining whether an individual belongs to an OWL concept is recognition.

Let's first look at recognition.  Recognition is the basic operation in
ShEx - we want to determine whether a particular node in an RDF graph matches
a ShEx shape, for example, to say that John in

\begin{ex}
  <John> foaf:name "John"^^xsd:string .
  <John> foaf:phone "+19085551212"^^xsd:string .
  <John> ex:child <Bill> .
  <John> ex:child <William> .
\end{ex}

matches

\begin{ex}
  { foaf:name xsd:string , foaf:phone xsd:string, ex:child [2] }
\end{ex}

Recognition is also a basic operation of OWL.

The OWL version of the above ShEx expression (using a version of the OWL-DL
publication syntax) is

\begin{ex}
    =1 foaf:name & all foaf:name xsd:string &
    =1 foaf:phone & all foaf:phone xsd:string &
    =2 ex:child
\end{ex}

So it seems that OWL can easily handle ShEx recognition.

However, John does not match the above OWL description.  Why is this?  It is
precisely that OWL does not assume that absence of information is
information about absence.  RDF works under the same assumptions, by the
way.  John could have more than one name as far as the above information is
concerned.   OWL (and RDF too) also does not assume that different names
refer to different individuals.  Bill and William could be the same person.

OWL has facilities to explicitly state information about absence and
information about differences.  If we add

\begin{ex}
    <John> in <=1 foaf:name .
    <John> in <=1 foaf:phone .
     <John> in all child {<Bill>, <William>} .
    <Bill> /= <William> .
\end{ex}

then John does match the above description.

So it is not that OWL does not perform the kind of recognition that
underlies ShEx, it is just that OWL does not make the assumption that
absence of information is information about absence.

However, suppose that we want to make this assumption.  This is roughly
equivalent to saying that a system assumes that if it can't determine some
fact, then that fact is false.  There is a very large body of work on this
topic because there are many tricky questions that arise with respect to
closure in any sophisticated formalism, and OWL is indeed sophisticated.

Fortunately RDF and RDFS are not very sophisticated at all, and the tricky
questions just do not arise if information comes in the form of RDF and RDFS
triples.  The basic idea is to treat the triples (and their RDF and RDFS
consequences if desired) as completely describing the world.  So, 1/ if a
triple is not present then it is false and 2/ different IRIs describe
different individuals.  This is precisely the same idea that underlies model
checking.  First-order inference is undecidable, but determining whether a
first-order sentence is true in one particular state of the world is much,
much easier.

So it is possible to use the OWL syntactic and semantic machinery to define
how to recognize OWL descriptions under just the same assumptions that
underlie ShEx.  The only change from the standard OWL setup is to define how
to go from an RDF graph to an OWL model.  (There are some technical details
that interfere with this general description of the account, but they are
easy to handle.)  Definitions, even recursive definitions, can be handled
with only minor extensions to the framework.

This is all quite easy and conforms to a common thread of both theoretical
and practical work.  It also matches how StarDog ICV works (as the
theoretical underpinning of StarDog ICV is one of these theoretical
results).  Further, the approach can be implemented by translation into
SPARQL queries, showing that it is practical.  (There may be some constructs
of OWL that do not translate into SPARQL queries when working with complete
information, but at least the parts of OWL that correspond to the usual
recognition conditions do so translate.)

-----

This mailing list provides plenty of evidence that OWL is not expressive 
enough and something on the level of SPARQL is needed. ShEx has an 
escape mechanism to fall back to SPARQL [1], and IBM has explicitly 
stated that this is required too [2].

So as a minimum, the outcome of 
this group should be to agree on a high-level vocabulary (possibly OWL 
and/or Shapes) plus a mechanism to represent other cases with something 
like SPARQL.

\subsection{Why OWL Closed World for RDF Validation?}

There are some key principles that need to be right. I believe that lack of the wider use of Semantic Web standards, has to do with a small handful of assumptions that ended up being obstacles instead of enablers. Commitment to the OWA to make monotonous reasoning possible, in my view, was one of them. On one hand, this decision has many implications that are too strange for people. On the other hand, monotonous reasoning is only possible when the asserted facts never change, just get added to. In real life, this rarely happens. Data often has errors which need to be corrected, facts that were true at some point get changed, etc. With this, the pluses of OWA don't seem to compensate for its minuses.

\subsection{Why NOT OWL Closed World for RDF Validation?}

- OWL cannot even do basic math

- OWL cannot do string operations

- OWL does not have have a concept of "variables" that is very much needed to do complex joins.

-----

Why is OWA and validation with OWL problematic (example)?

As for an area where OWA is problematic, one need look no further than
FRBRer ontology[1], which is clearly designed using OWL constraints
(which I prefer to call "axioms" to avoid confusion) in a closed world
way. The definitions are quite strict, with all classes disjoint each
other, such that, using reasoning in the OW, any FRBRer data will be
inconsistent with data not using that exact set of axioms.

We used a FRBRer dataset as a use case in the main RDFUnit paper [1] and we actually came to the same conclusions.
[1] http://svn.aksw.org/papers/2014/WWW_Databugger/public.pdf

\subsection{Discussion Why (NOT) OWL Closed World for RDF Validation?}

ambiguousness:
Reusing OWL syntax with a closed world interpretation is of course a seductive path but I've always been a bit uneasy about it. OWA is built in the OWL Recommendation. I would rather have a neutral language, with non-ambiguous open world interpretation in OWL, and another one in any closed-world language (SPIN, SPARQL, you name it).

Yeah, I appreciate that concern. Everyone keeps telling me that this seems like a problem in principle; apparently we're the only ones who built it *as a real thing* and *in practice* it's not a problem at all. Our customers don't find it in the least bit confusing. In fact, as we originally said, most people who wanted OWL always wanted closed world semantics anyway, so giving it to them is a big win.
Would using different namespaces help in acceptance?
NO → to not break existing tools like Protege which knew how to manipulate that *syntax*
YES → avoid confusion

\subsection{Unique Naming Assumption}

Non-Unique Naming Assumption
You can't easily use OWL to even do cardinality checking. For example, suppose you assert that :hasFather is a functional property, and you have the triples :Luke :hasFather :Anakin and :Luke :hasFather :Darth.An OWL reasoner will invoke the Non-Unique Naming Assumption to infer that :Anakin owl:sameAs :Darth.

\section{Modularize and Separate Semantics and Constraints}

semantics (OWL ontologies)

In some cases, inferred triples are not intended or do not make sense within a specific application.

\textbf{Constraints are application-specific.}
When combining terms from multiple sources, 
the constraints associated with a term often depend on how 
the term is used in a particular application. Consider DC Terms. It was 
designed to provide a highly reusable vocabulary. There are very few 
constraints imposed by DC Terms and this makes it very reusable. For 
example, consider dcterms:title. In one application dcterms:title may be a 
required property while in another it may be optional. So where do you put 
those constraints? They do not belong in the DC Terms vocabulary. You need 
another place to define constraints and associate them with the 
application.

Different consumers of information conforming to an ontology may want
different constraints to be checked against that ontology.

\textbf{Inferencing and Constraint Validation.}
So if you use RDFS and OWL, and include a lot of constraints, then the 
terms are not very reusable because they carry a lot of baggage in the 
form of inferences which may not make sense in your application. For 
example, if you used rdfs:domain or rdfs:range then you infer certain type 
triples. I once was looking for terms that defined start and stop dates. I 
found dtstart and dtend in http://www.w3.org/2002/12/cal/ical but when I 
looked at the RDFS/OWL it had a lot of undesired inferences concerning the 
domain. So if I had reused dtstart in my application, then a reasoner 
would have inferred a lot of triples that didn't make sense.

\textbf{Reuse of Terms from Vocabularies.}
At OSLC we are trying to integrate information from a lot of applications. 
We try to reuse terms from established vocabularies. We define new common 
terms in a core OSLC vocabulary. We do this to make writing queries 
easier. This means that resources contain terms from many vocabularies.

%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0301.html}}

\textbf{Modularization of ontologies and constraints.}

All these complaints about RDFS and OWL appear to be based on the conception 
that RDFS and OWL work with a single document containing everything that can 
ever be said about a particular vocabulary.

However, this is a misconception.  It is certainly possible in RDFS and OWL to 
have multiple documents that speak to the same vocabulary.  This is done, for 
example, when OWL ontologies are extended.  A core document talks about the 
core vocabulary and other documents add new vocabulary and add new information 
about the core vocabulary as well.

The exact same thing can (and should) be done with constraints.  You can have 
a document that provides the core information about a vocabulary.  You can 
have multiple documents that provide constraints on this vocabulary for 
various purposes.  When validating some information one can pick which set or 
sets of constraints to apply.

This division can also be done with the axioms of the ontology.  There is no 
need for all the axioms of an ontology to be in the same document, leading to 
the possibility of having the RDFS portion be in one document and the non-RDFS 
portion in another document.  Other divisions are also possible.

[Assume w.l.o.g. that we are only considering standardized OWL semantics.*]
If an axiom is part of the core meaning of a term then it belongs in the core  ontology.  For example, if it is part of the definition of the term  'bicycle' in the ontology that it must have exactly two wheels, this axiom belongs in the core ontology. Unicycles are thus excluded.

Bicycles with 'training wheels' attached may or may not qualify, based on how 'training wheels' are defined.  
Removing a core axiom from the ontology does not provide more opportunities for *reuse* ; it provides more opportunities for *misuse*.
If an axiom is not part of the core meaning of a term, then it does not belong in the core ontology.  If there are no meaningful cardinality constraints on the number of titles a thing can have then they don't belong in the core ontology.
Fortunately it is possible to build new, more restrictive ontologies that reuse and restrict existing ontologies. If one wishes to describe a world where bicycles can only have wheels with spokes (e.g.  things with solid wheels are not within the meaning of 'bicycle') , one can use an import statement to include the axioms from another ontology, then add the additional axioms that commitments only in this new ontology.

If you are engaged in an information fusion task, the more precise the definitions used in the shared ontology, the more feasible the task becomes.  The more diverse the information contexts become the less useful generic terms become.
Having a broad  property named "health" is useless if in one part of the organization it refers to having up to date vaccinations , and in another it refers to the whether an aircraft is ready to deploy.
%\footnote{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0305.html}}

\textbf{separate declarations (shapes, constraints) and OWL restrictions (semantics).}
The declarations of classes, properties and instances can happen in one graph, 
and then there can be 
multiple interpretations, including specifications in multiple 
languages. OWL already has owl:imports, SPIN already has spin:imports, 
ICV has ic:imports. RDF should probably have rdf:imports (and rdf:Graph 
similar to owl:Ontology).

I guess the question remains is what to do with the published 
vocabularies that do not honor this separation and mix the OWL 
restrictions and class definitions into a single file. Even rdfs:domain 
and range statements are often too restrictive. One answer is to simply 
ignore those statements and start with the languages in the right hand 
side of the diagram. After all, an rdfs:domain statement is just another 
triple. But there will be applications where mixing Shapes or SPIN with 
OWL semantics is desirable. There is no single truth here, and the 
application developer is already allowed to choose.

%\footnote{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0306.html}}

-----

Our suggestion:
Separate facts, axioms, and constraints

- documents containing facts (import other documents)
- documents containing OWL axioms / semantics / ontology
- documents containing constraints

\subsection{difference between ontologies and constraints}

To make an analogy with natural language, we have words and they are 
defined in a dictionary. We also have grammars and they define how the 
words are combined. We have the general rules of grammar for ordinary 
prose. We also have other types of grammars for specialized texts such as 
poetry. There are rules for sonnets, limericks, etc. The dictionary is 
analogous to the RDFS or OWL document. The grammar is analogous to a Shape 
document.

\subsection{vocabularies/ontologies and constraints are independent}

create / maintain / control vocabularies/ontologies and constraints independently

They (and I) want one party to create and maintain a
vocabulary/ontology, while multiple other (unrelated) parties are able
to create and maintain reusable sets of constraints involving that
vocabulary (and not violating the constraints in that ontology).

difference between ontology and vocabulary

They presume something which perhaps you do not, which is that the
party which hosts the IRIs comprising a vocabulary is empowered to
maintain the definitive ontology for that vocabulary.  That's why I
wrote "vocabulary/ontology", because with this Linked Data approach, the
two go together.  I think this approach is widely accepted, although I
don't think it's explicit in any W3C Recommendation.

What I hear you saying here is that regardless of that, it's reasonable
for other people to publish/maintain what we might call a "secondary" or
"third-party" ontology, which contains axioms concerning someone else's
vocabulary.    My sense is this kind of thing is generally regarded as a
Bad Practice, although I don't offhand know why, and there might not be
any good reason.  I think I've seen people yelled at for suggesting
something like this (which doesn't necessarily mean it's a bad idea).

For my use case, I think the important thing is to be able to attach
constraints to interfaces.  To simplify somewhat, I want to say when
you're POSTing to URL U, if you want things to work properly, you MUST
include exactly one foaf:firstName on each instance of foaf:Person.

I can imagine writing that as:

    <U> eg:interfaceConstraints <UC>

and then <UC> would contain OWL of the form:

    foaf:Person owl:subClassOf [
       a owl:Restriction;
       owl:cardinality 1;
       owl:onProperty foaf:firstName
    ].

I don't really know Manchester syntax, but maybe it would be something like:

    Class: foaf:Person
       Types: foaf:firstName exactly 1

Is that how you would propose I get the functionality I want?

Somewhere I'd need to say that this OWL is to be understood with closed
world semantics, right?

Are there other problems I might have?

-----

\textbf{axioms restricting base ontologies}

It is absolutely normal to assert axioms in an ontology that restrict the models of terms in another ontology. It's an important part of ontology modularity.
Think about all the axioms that are defined on Thing and Nothing.
The key things to realize is that these axioms *only hold for that ontology*, and that statements made that are true in the restricted ontology are true in the unrestricted ontology, but not vice versa.  
*ANY* method you use to constrain the set of things that some ontology allows to exist is *BY DEFINITION* creating a new ontology using the terms of the original.

\textbf{constraints and vocabularies/ontologies are dependent}

One can argue that particular vocabularies/ontologies should permit multiple sets of constraints.  I agree with this argument.  This does not make the constraints independent of the vocabulary or ontology, however.  In fact, every example of ShEx that I have seen is very tied to a particular vocabulary.

use of OWL for validation:

(1) import base ontology + add. axioms

(2) import set of constraints (for different uses)

OWL and RDFS do not fail on this point at all.  One can use OWL and RDFS in a very flexible manner, where there is a base ontology and additional axioms.  A constraint system using OWL or RDFS can work in a similar fashion.

Even StarDog ICV can be used in this manner.  All you have to do is have an overall file that imports the base ontology and separately constraint-imports the constraints.  Different uses can have the same ontology and different constraints.  Some uses can even have just the constraints.  One could also have a trivial modification of StarDog ICV that had an extra explicit input - the constraints.

\section{Diskussionen}

Man müsste mit der Behauptung "vollständig gegen OWL 2 Konstrukte"
vorsichtig sein, in einer gewissen Lesart von Vollständigkeit bist du
vielleicht nicht vollstädnig. Überprüfts du auch so Sachen, die sich
durch folgende Konmbination an Axiomen und Assertions ergeben? Hier ein
Beispiel.

\begin{align*}

(1) \exists teachesStudent.\top \sqsubseteq TeacherUniversity

(2) TeacherUniversity \sqsubseteq EmployeeUniversity

(3) EmployeeUniversity \sqsubseteq \neg EmployeeCompany

(4) teachesStudent(eckert,schmidt)

(5) EmployeeCompany(eckert)

(1)+4) = (6) TeacherUniversity(eckert)

(6) + (2) = (7) EmployeeUniversity(eckert)

(7) + (3) = (8) \neg EmployeeCompany(eckert)
\end{align*}

(8) und (5) sind im direkten Widerspruch. Das Problem ist hier dass
Reasoning und Constraints sozusagen zusammenarbeiten, und mir ist kein
Ansatz bekannt, der das Reasoning für OWL 2 in Query Rewriting erledigen
kann.

Aber vielleicht wird das Beispiel ja tatsächlich von deinem Ansatz
erwischt (tatsächlichkann man etwas definieren, was für dieses Beispiel
vollständig ist = etwas was für DL lite vollständig ist, wenn ich grade
nix falsch sehe).

\section{Validation in RDF, XML, and Relational Worlds}

\subsection{Similarities}

\subsection{Differences}

\textbf{Difference between XML world and RDF world}
XML document with correct syntax->Well-formed

XML document with correct syntax and accomplishing with a DTD|XML Schema->Well-formed and Valid

check if a RDF graph is "well formed" (RDF syntax, etc.)

check if the RDF graph is *valid* under a certain taste RDFS, OWLx, etc. (integrity and cardinality constraints, etc with a reasoner, SPIN, etc.) (for instance cardinality of properties and data types)

\section{Related Work}

\begin{itemize}
	\item See e.g. chapter 6 of Jiao Tao's dissertation - http://tw.rpi.edu/web/doc/JiaoTaoDissertation .
\end{itemize}

\textbf{CWA.}

alternate semantics for OWL (using CWA):

Several years ago Evren Siren et al proposed an alternate semantics for OWL (using CWA) so that it could be used for integrity constraint (IC) checking and this is implemented in the Stardog database.

However, this OWL IC semantics was never submitted to a standards organization.

\section{Conclusion and Future Work}

\bibliography{literatur}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2014-09-19 paper/paper1.tex
Disjoint Group of Properties (Class-Specific)

@@
 
+\section{Requirements Not Expressible By OWL 2 QL}
+
+\subsection{Class-Specific Disjoint Group of Properties}
+
+requirements DB:
+\begin{itemize}
+  \item ID: R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
+	\item URL: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/20}
+\end{itemize}
+
+A \textless Human\textgreater has either a name or at least 1 given name and 1 family name.
+
+constraint (ShEx):
+
+\begin{ex}
+<Human> {                           
+    (                                    
+            foaf:name xsd:string              
+        |                                   
+            foaf:givenName xsd:string+,      
+            foaf:familyName xsd:string
+    )
+}
+\end{ex}
+
+valid data (ShEx):
+
+\begin{ex}
+<Anakin>
+    foaf:givenName "Anakin" ;
+    foaf:familyName "Skywalker" .
+\end{ex}
+
+\begin{ex}
+<Anakin>
+    foaf:name "Anakin Skywalker" .
+\end{ex}
+
+invalid data (ShEx):
+
+\begin{ex}
+<Anakin>
+    foaf:givenName "Anakin" ;
+    foaf:familyName "Skywalker" ;
+    foaf:name "Anakin Skywalker" .
+\end{ex}
+
 \section{Related Work}

### 2014-09-22 paper/paper1.tex
OWL 2 QL

@@
 
-\section{Idea}
+\section{Ideas}
 
@@
 
+\tb{should we provide an implementation of RDF Validation with OWL 2 QL in the RDF Validator (purl.org/net/rdfval-demo)?}
+
 \section{research questions}
@@
 
-\section{Requirements Not Expressible By OWL 2 QL}
+\section{OWL 2 QL}
+
+OWL 2 profiles specification: \cite{owl2profiles2008}
+
+\begin{itemize}
+  \item OWL 2 QL constructs
+	\item Difference between OWL 2 DL and OWL 2 QL
+\end{itemize}
+
+\section{RDF Validation Requirements Expressible By OWL 2 QL}
+
+\section{RDF Validation Requirements Not Expressible By OWL 2 QL}
+
+\subsection{class-specific disjoint data properties}
+
+constraint (ShEx):
+
+\begin{ex}
+(foaf:name xsd:string  | foaf:givenName xsd:string+, foaf:familyName xsd:string)
+\end{ex}
+
+\subsection{class-specific disjoint object properties}
 

### 2014-09-22 paper/paper1.tex
OWL 2 QL supported and not supported constructs

@@
 
-\tb{should we provide an implementation of RDF Validation with OWL 2 QL in the RDF Validator (purl.org/net/rdfval-demo)?}
-
 \section{research questions}
@@
 	\item Difference between OWL 2 DL and OWL 2 QL
+\end{itemize}
+
+\textbf{Logical Underpinning for OWL 2 QL.}
+OWL 2 QL is based on the DL-Lite family of description logics.
+Several variants of DL-Lite have been described in the literature, and DL-Lite$_R$ provides the logical underpinning for OWL 2 QL.
+DL-Lite$_R$ does not require the unique name assumption (UNA), since making this assumption would have no impact on the semantic consequences of a DL-Lite$_R$ ontology.
+More expressive variants of DL-Lite, such as DL-Lite$_A$, extend DL-Lite$_R$ with functional properties, and these can also be extended with keys; however, for query answering to remain in LOGSPACE, these extensions require UNA and need to impose certain global restrictions on the interaction between properties used in different types of axiom.
+Basing OWL 2 QL on DL-Lite$_R$ avoids practical problems involved in the explicit axiomatization of UNA \cite{owl2profiles2008}.
+
+\subsection{allowed usage of constructs in class expressions}
+
+\textbf{Subclass Expressions}
+
+\begin{itemize}
+	\item class
+  \item ObjectSomeValuesFrom (where the class is limited to owl:Thing)
+  \item DataSomeValuesFrom
+\end{itemize}
+
+\textbf{Superclass Expressions}
+
+\begin{itemize}
+	\item class
+  \item ObjectIntersectionOf
+  \item ObjectComplementOf
+  \item ObjectSomeValuesFrom
+  \item DataSomeValuesFrom
+\end{itemize}
+
+\subsection{supported constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item subclass axioms (SubClassOf)
+  \item class expression equivalence (EquivalentClasses)
+  \item class expression disjointness (DisjointClasses)
+  \item inverse object properties (InverseObjectProperties)
+  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
+  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
+  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
+  \item property range (ObjectPropertyRange and DataPropertyRange)
+  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
+  \item symmetric properties (SymmetricObjectProperty)
+  \item reflexive properties (ReflexiveObjectProperty)
+  \item irreflexive properties (IrreflexiveObjectProperty)
+  \item asymmetric properties (AsymmetricObjectProperty)
+  \item assertions other than individual equality assertions and negative property assertions (DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion) 
+\end{itemize}
+
+\subsection{not supported constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
+  \item self-restriction (ObjectHasSelf)
+  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
+  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
+  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
+  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
+  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
+  \item property inclusions (SubObjectPropertyOf) involving property chains
+  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
+  \item transitive properties (TransitiveObjectProperty)
+  \item keys (HasKey)
+  \item individual equality assertions and negative property assertions
 \end{itemize}

### 2014-09-22 paper/paper1.tex
OWL 2 QL supported and not supported constructs

@@
 
+\section{Appendix}
+
+\subsection{RDF Validation Requirements Covered by OWL 2 QL}
+
+\begin{table}
+\caption{RDF Validation Requirements Covered by OWL 2 QL}
+\label{tab:RequirementsCoveredOWL2QL}
+\centering
+\begin{tabular}{lcccccccc}
+\hr
+Requirements \\
+\hr
+R-1-UNIQUENESS-OF-URIS \\
+R-2-UNIQUE-INSTANCES \\
+R-3-EQUIVALENT-CLASSES \\
+R-4-EQUIVALENT-OBJECT-PROPERTIES \\
+R-5-EQUIVALENT-DATA-PROPERTIES \\
+\hr
+\end{tabular}
+\end{table}
+
+\subsection{RDF Validation Requirements Not Covered by OWL 2 QL}
+
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
+\label{tab:RequirementsNotCoveredOWL2QL}
+\centering
+\begin{tabular}{lcccccccc}
+\hr
+Requirements \\
+\hr
+R-6-EQUIVALENT-INDIVIDUALS \\
+\hr
+\end{tabular}
+\end{table}
+
 \bibliography{literatur}{}

### 2014-09-22 paper/paper1.tex
appendix

@@
 
-\subsection{allowed usage of constructs in class expressions}
-
-\textbf{Subclass Expressions}
-
-\begin{itemize}
-	\item class
-  \item ObjectSomeValuesFrom (where the class is limited to owl:Thing)
-  \item DataSomeValuesFrom
-\end{itemize}
-
-\textbf{Superclass Expressions}
-
-\begin{itemize}
-	\item class
-  \item ObjectIntersectionOf
-  \item ObjectComplementOf
-  \item ObjectSomeValuesFrom
-  \item DataSomeValuesFrom
-\end{itemize}
-
-\subsection{supported constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item subclass axioms (SubClassOf)
-  \item class expression equivalence (EquivalentClasses)
-  \item class expression disjointness (DisjointClasses)
-  \item inverse object properties (InverseObjectProperties)
-  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
-  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
-  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
-  \item property range (ObjectPropertyRange and DataPropertyRange)
-  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
-  \item symmetric properties (SymmetricObjectProperty)
-  \item reflexive properties (ReflexiveObjectProperty)
-  \item irreflexive properties (IrreflexiveObjectProperty)
-  \item asymmetric properties (AsymmetricObjectProperty)
-  \item assertions other than individual equality assertions and negative property assertions (DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion) 
-\end{itemize}
-
-\subsection{not supported constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
-  \item self-restriction (ObjectHasSelf)
-  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
-  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
-  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
-  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
-  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
-  \item property inclusions (SubObjectPropertyOf) involving property chains
-  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
-  \item transitive properties (TransitiveObjectProperty)
-  \item keys (HasKey)
-  \item individual equality assertions and negative property assertions
-\end{itemize}
-
-\section{RDF Validation Requirements Expressible By OWL 2 QL}
-
-\section{RDF Validation Requirements Not Expressible By OWL 2 QL}
+\section{RDF Validation Requirements Not Covered By OWL 2 QL}
 
@@
 
+\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
+
+\textbf{Subclass Expressions}
+
+\begin{itemize}
+	\item class
+  \item ObjectSomeValuesFrom (where the class is limited to owl:Thing)
+  \item DataSomeValuesFrom
+\end{itemize}
+
+\textbf{Superclass Expressions}
+
+\begin{itemize}
+	\item class
+  \item ObjectIntersectionOf
+  \item ObjectComplementOf
+  \item ObjectSomeValuesFrom
+  \item DataSomeValuesFrom
+\end{itemize}
+
+\subsection{Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item subclass axioms (SubClassOf)
+  \item class expression equivalence (EquivalentClasses)
+  \item class expression disjointness (DisjointClasses)
+  \item inverse object properties (InverseObjectProperties)
+  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
+  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
+  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
+  \item property range (ObjectPropertyRange and DataPropertyRange)
+  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
+  \item symmetric properties (SymmetricObjectProperty)
+  \item reflexive properties (ReflexiveObjectProperty)
+  \item irreflexive properties (IrreflexiveObjectProperty)
+  \item asymmetric properties (AsymmetricObjectProperty)
+  \item assertions other than individual equality assertions and negative property assertions (DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion) 
+\end{itemize}
+
+\subsection{Not Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
+  \item self-restriction (ObjectHasSelf)
+  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
+  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
+  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
+  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
+  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
+  \item property inclusions (SubObjectPropertyOf) involving property chains
+  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
+  \item transitive properties (TransitiveObjectProperty)
+  \item keys (HasKey)
+  \item individual equality assertions and negative property assertions
+\end{itemize}
+
 \subsection{RDF Validation Requirements Covered by OWL 2 QL}
@@
 \centering
-\begin{tabular}{lcccccccc}
+\begin{tabular}{ll}
 \hr
-Requirements \\
+Requirements Classification & Requirements \\
 \hr
-R-1-UNIQUENESS-OF-URIS \\
-R-2-UNIQUE-INSTANCES \\
-R-3-EQUIVALENT-CLASSES \\
-R-4-EQUIVALENT-OBJECT-PROPERTIES \\
-R-5-EQUIVALENT-DATA-PROPERTIES \\
+& R-1-UNIQUENESS-OF-URIS \\
+& R-2-UNIQUE-INSTANCES \\
+& R-3-EQUIVALENT-CLASSES \\
+& R-4-EQUIVALENT-OBJECT-PROPERTIES \\
+& R-5-EQUIVALENT-DATA-PROPERTIES \\
+& R-7-DISJOINT-CLASSES \\
+& R-9-DISJOINT-OBJECT-PROPERTIES \\
+& R-10-DISJOINT-DATA-PROPERTIES \\
+& R-14-DISJOINT-INDIVIDUALS \\
 \hr
@@
 \centering
-\begin{tabular}{lcccccccc}
+\begin{tabular}{lc}
 \hr
-Requirements \\
+Requirements & Covering Constraint Languages \\
 \hr
-R-6-EQUIVALENT-INDIVIDUALS \\
+R-6-EQUIVALENT-INDIVIDUALS & OWL 2 DL \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS & OWL 2 DL \\
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
 \hr

### 2014-09-22 paper/paper1.tex
supported requirements

@@
 
-\begin{itemize}
-	\item class
-  \item ObjectSomeValuesFrom (where the class is limited to owl:Thing)
-  \item DataSomeValuesFrom
-\end{itemize}
+\begin{ex}
+subClassExpression :=
+    Class |
+    subObjectSomeValuesFrom | DataSomeValuesFrom
+subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
+\end{ex}
 
@@
 
-\begin{itemize}
-	\item class
-  \item ObjectIntersectionOf
-  \item ObjectComplementOf
-  \item ObjectSomeValuesFrom
-  \item DataSomeValuesFrom
-\end{itemize}
+\begin{ex}
+superClassExpression :=
+    Class |
+    superObjectIntersectionOf | superObjectComplementOf |
+    superObjectSomeValuesFrom | DataSomeValuesFrom
+\end{ex}
 
@@
 & R-2-UNIQUE-INSTANCES \\
-& R-3-EQUIVALENT-CLASSES \\
-& R-4-EQUIVALENT-OBJECT-PROPERTIES \\
-& R-5-EQUIVALENT-DATA-PROPERTIES \\
-& R-7-DISJOINT-CLASSES \\
-& R-9-DISJOINT-OBJECT-PROPERTIES \\
-& R-10-DISJOINT-DATA-PROPERTIES \\
-& R-14-DISJOINT-INDIVIDUALS \\
+& R-3-EQUIVALENT-CLASSES (EquivalentClasses) \\
+& R-4-EQUIVALENT-OBJECT-PROPERTIES (EquivalentObjectProperties) \\
+& R-5-EQUIVALENT-DATA-PROPERTIES (EquivalentDataProperties) \\
+& R-7-DISJOINT-CLASSES (DisjointClasses) \\
+& R-9-DISJOINT-OBJECT-PROPERTIES (DisjointObjectProperties) \\
+& R-10-DISJOINT-DATA-PROPERTIES (DisjointDataProperties) \\
+& R-14-DISJOINT-INDIVIDUALS (DifferentIndividuals) \\
+& R-25-OBJECT-PROPERTY-DOMAIN (ObjectPropertyDomain) \\
+& R-26-DATA-PROPERTY-DOMAIN (DataPropertyDomain) \\
+& R-27-CLASS-SPECIFIC-VALIDATION \\
+& R-28-OBJECT-PROPERTY-RANGE (ObjectPropertyRange) \\
 \hr
@@
 \hr
-R-6-EQUIVALENT-INDIVIDUALS & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS & OWL 2 DL \\
+R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
 R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
@@
 R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (ObjectUnionOf) & OWL 2 DL \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPARQL, SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPARQL, SPIN \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPARQL, SPIN \\
+R-24-PROVENANCE-CONSTRAINTS & \\
 \hr

### 2014-09-23 paper/paper1.tex
requirements not covered by OWL 2 QL

--- 2014-09-22 paper/paper1.tex
@@
 
-\subsection{class-specific disjoint data properties}
+\subsection{Class-Specific Disjointness of Properties}
+
+requirements:
+
+\begin{itemize}
+	\item R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
+  \item R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC
+  \item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
+\end{itemize}
+
+\textbf{class-specific disjoint data properties}
 
@@
 
-\subsection{class-specific disjoint object properties}
+\textbf{class-specific disjoint object properties}
 
-\subsection{Class-Specific Disjoint Group of Properties}
+\textbf{Class-Specific Disjoint Group of Properties}
 
@@
 
+\subsection{Default Values}
+
+requirements:
+
+\begin{itemize}
+	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
+  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
+\end{itemize}
+
+\subsection{Membership in Controlled Vocabularies}
+
+requirements:
+
+\begin{itemize}
+	\item R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES
+	\item R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES
+\end{itemize}
+
+\subsection{Pattern Matching}
+
+requirements:
+
+\begin{itemize}
+	\item R-21
+	\item R-22
+	\item R-23
+	\item R-44
+	\item R-141
+\end{itemize}
+
 \section{Related Work}
@@
 & R-2-UNIQUE-INSTANCES \\
-& R-3-EQUIVALENT-CLASSES \\
-& R-4-EQUIVALENT-OBJECT-PROPERTIES \\
-& R-5-EQUIVALENT-DATA-PROPERTIES \\
-& R-7-DISJOINT-CLASSES \\
-& R-9-DISJOINT-OBJECT-PROPERTIES \\
-& R-10-DISJOINT-DATA-PROPERTIES \\
-& R-14-DISJOINT-INDIVIDUALS \\
+& R-3-EQUIVALENT-CLASSES (EquivalentClasses) \\
+& R-4-EQUIVALENT-OBJECT-PROPERTIES (EquivalentObjectProperties) \\
+& R-5-EQUIVALENT-DATA-PROPERTIES (EquivalentDataProperties) \\
+& R-7-DISJOINT-CLASSES (DisjointClasses) \\
+& R-9-DISJOINT-OBJECT-PROPERTIES (DisjointObjectProperties) \\
+& R-10-DISJOINT-DATA-PROPERTIES (DisjointDataProperties) \\
+& R-14-DISJOINT-INDIVIDUALS (DifferentIndividuals) \\
+& R-25-OBJECT-PROPERTY-DOMAIN (ObjectPropertyDomain) \\
+& R-26-DATA-PROPERTY-DOMAIN (DataPropertyDomain) \\
+& R-27-CLASS-SPECIFIC-VALIDATION \\
+& R-28-OBJECT-PROPERTY-RANGE (ObjectPropertyRange) \\
+& R-35-DATA-PROPERTY-RANGE (DataPropertyRange) \\
 \hr
@@
 R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (ObjectUnionOf) & OWL 2 DL \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPARQL, SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPARQL, SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPARQL, SPIN, ShEx \\
+R-24-PROVENANCE-CONSTRAINTS & \\
+R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
+R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
+R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
+R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
+R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
+R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
+R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
 \hr

### 2014-09-23 paper/paper1.tex
R-45 - R-49

@@
 \begin{itemize}
-	\item R-21
-	\item R-22
-	\item R-23
-	\item R-44
-	\item R-141
+	\item R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS
+  \item R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS
+  \item R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES
+  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
+  \item R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS
+\end{itemize}
+
+\subsection{Calculations on and Comparisons of RDF Literals}
+
+requirements:
+
+\begin{itemize}
+	\item R-41-STATISTICAL-COMPUTATIONS
+	\item R-42-COMPUTATIONS-BASED-ON-DATATYPE
+	\item R-43-COMPARISONS-BASED-ON-DATATYPE
+\end{itemize}
+
+\subsection{Constraining Facets on RDF Literals}
+
+requirements:
+
+\begin{itemize}
+	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
+  \item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
+	\item R-46-CONSTRAINING-FACETS
+\end{itemize}
+
+\subsection{Language of RDF Literals}
+
+requirements:
+
+\begin{itemize}
+	\item R-47-LANGUAGE-TAG-MATCHING
+  \item R-48-MISSING-LANGUAGE-TAGS
+	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
 \end{itemize}
@@
 R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPARQL, SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPARQL, SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPARQL, SPIN, ShEx \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
 R-24-PROVENANCE-CONSTRAINTS & \\
@@
 R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
+R-41-STATISTICAL-COMPUTATIONS & SPIN \\
+R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
+R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
+R-47-LANGUAGE-TAG-MATCHING & SPIN \\
+R-48-MISSING-LANGUAGE-TAGS & SPIN \\
+R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
+R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
 \hr

### 2014-09-23 paper/paper1.tex
R-50 - R-67

@@
 	\item R-46-CONSTRAINING-FACETS
+	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
 \end{itemize}
@@
 	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
+\end{itemize}
+
+\subsection{Property Occurrences}
+
+requirements:
+
+\begin{itemize}
+	\item R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
+	\item R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
+	\item R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE
+\end{itemize}
+
+\subsection{Property Groups}
+
+requirements:
+
+\begin{itemize}
+	\item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
+	\item R-66-PROPERTY-GROUPS
 \end{itemize}
@@
 & R-35-DATA-PROPERTY-RANGE (DataPropertyRange) \\
+& R-54-SUB-OBJECT-PROPERTIES (SubObjectPropertyOf) \\
+& R-56-INVERSE-OBJECT-PROPERTIES (ObjectInverseOf) \\
+& R-59-REFLEXIVE-OBJECT-PROPERTIES (ReflexiveObjectProperty) \\
+& R-60-IRREFLEXIVE-OBJECT-PROPERTIES (IrreflexiveObjectProperty) \\
+& R-61-SYMMETRIC-OBJECT-PROPERTIES (SymmetricObjectProperty) \\
+& R-62-ASYMMETRIC-OBJECT-PROPERTIES (AsymmetricObjectProperty) \\
+& R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
 \hr
@@
 R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
+R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
+R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
+R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
+R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
+R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
+R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\

### 2014-09-23 paper/paper1.tex
R-68 - R-85

@@
 \documentclass{llncs}
+
+% allows for temporary adjustment of side margins
+\usepackage{chngpage}
+
+% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
+\usepackage{booktabs}
 
@@
 
+%\medskip% adds some space before the table
+%\begin{adjustwidth}{-1in}{-1in}% adjust the L and R margins by 1 inch
+  %\begin{tabular}{ll}
+    %\toprule
+    %Requirements & Covering Constraint Languages \\
+    %\midrule
+%R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
+%R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
+%R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+%R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+%R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+%R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+%R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+%R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (ObjectUnionOf) & OWL 2 DL \\
+%R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+%R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+%R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+%R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
+%R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+%R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
+%R-24-PROVENANCE-CONSTRAINTS & \\
+%R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
+%R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
+%R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
+%R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+%R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
+%R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+%R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+%R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
+%R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
+%R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+%R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
+%R-41-STATISTICAL-COMPUTATIONS & SPIN \\
+%R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
+%R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+%R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+%R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
+%R-47-LANGUAGE-TAG-MATCHING & SPIN \\
+%R-48-MISSING-LANGUAGE-TAGS & SPIN \\
+%R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
+%R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
+%R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
+%R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+%R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+%R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
+%R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
+%R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
+%R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
+%R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
+%R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+%R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+%R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+%R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+%R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+%R-71-CONDITIONAL-PROPERTIES \\
+%R-72-RECOMMENDED-PROPERTIES \\
+%R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+%R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+%R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
+%R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+    %\bottomrule
+  %\end{tabular}
+%\end{adjustwidth}
+%\medskip% adds some space after the table
+
 \begin{table}
 \caption{RDF Validation Requirements Not Covered by OWL 2 QL}
-\label{tab:RequirementsNotCoveredOWL2QL}
+\label{tab:RequirementsNotCoveredOWL2QL-1}
 \centering
-\begin{tabular}{lc}
+\begin{tabular}{ll}
 \hr
@@
 R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-71-CONDITIONAL-PROPERTIES \\
+R-72-RECOMMENDED-PROPERTIES \\
+\hr
+\end{tabular}
+\end{table}
 
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
+\label{tab:RequirementsNotCoveredOWL2QL-2}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements & Covering Constraint Languages \\
+\hr
+R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
+\label{tab:RequirementsNotCoveredOWL2QL-3}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements & Covering Constraint Languages \\
+\hr
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\

### 2014-09-23 paper/paper1.tex
R-86 - R-92

@@
 \hr
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\

### 2014-09-24 paper/paper1.tex
R-93 - R-126

--- 2014-09-23 paper/paper1.tex
@@
 
+\subsection{RDF-Specific Validation}
+
+requirements:
+
+\begin{itemize}
+	\item R-120-HANDLE-RDF-COLLECTIONS
+\end{itemize}
+
+\subsection{RDF Shapes}
+
+requirements:
+
+\begin{itemize}
+	\item R-125-RDF-SHAPE-CHECKING
+\end{itemize}
+
 \section{Related Work}
@@
 
-evaluation using practical data set
-
-\section{Conclusion and Future Work}
-
-\section{Appendix}
-
-\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
-
-\textbf{Subclass Expressions}
-
-\begin{ex}
-subClassExpression :=
-    Class |
-    subObjectSomeValuesFrom | DataSomeValuesFrom
-subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
-\end{ex}
-
-\textbf{Superclass Expressions}
-
-\begin{ex}
-superClassExpression :=
-    Class |
-    superObjectIntersectionOf | superObjectComplementOf |
-    superObjectSomeValuesFrom | DataSomeValuesFrom
-\end{ex}
-
-\subsection{Supported Constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item subclass axioms (SubClassOf)
-  \item class expression equivalence (EquivalentClasses)
-  \item class expression disjointness (DisjointClasses)
-  \item inverse object properties (InverseObjectProperties)
-  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
-  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
-  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
-  \item property range (ObjectPropertyRange and DataPropertyRange)
-  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
-  \item symmetric properties (SymmetricObjectProperty)
-  \item reflexive properties (ReflexiveObjectProperty)
-  \item irreflexive properties (IrreflexiveObjectProperty)
-  \item asymmetric properties (AsymmetricObjectProperty)
-  \item assertions other than individual equality assertions and negative property assertions (DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion) 
-\end{itemize}
-
-\subsection{Not Supported Constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
-  \item self-restriction (ObjectHasSelf)
-  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
-  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
-  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
-  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
-  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
-  \item property inclusions (SubObjectPropertyOf) involving property chains
-  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
-  \item transitive properties (TransitiveObjectProperty)
-  \item keys (HasKey)
-  \item individual equality assertions and negative property assertions
-\end{itemize}
+\subsection{Evaluation Using Practical Data Set}
 
 \subsection{RDF Validation Requirements Covered by OWL 2 QL}
+
+Table~\ref{tab:RequirementsCoveredOWL2QL}
 
@@
 & R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
+& R-93-DIFFERENCE-BETWEEN-CONSTRAINTS-ON-OBJECT-AND-DATA-PROPERTIES \\
+& R-94-POSITIVE-OBJECT-PROPERTY-ASSERTIONS (ObjectPropertyAssertion) \\
+& R-95-POSITIVE-DATA-PROPERTY-ASSERTIONS (DataPropertyAssertion) \\
+& R-99-STABLE-IDENTIFICATION-OF-CONSTRAINTS \\
+& R-100-SUBSUMPTION (SubClassOf) \\
+& R-101-DECLARATIVE-CONSTRAINT-LANGUAGE \\
+& R-102-INTUITIVE-CONSTRAINT-LANGUAGE \\
+& R-103-HIGH-LEVEL-CONSTRAINT-LANGUAGE \\
+& R-104-CONSTRAINT-LANGUAGE-HAVING-IMPLEMENTATION-LANGUAGE \\
+& R-105-CONSTRAINT-LANGUAGE-TRANSLATABLE-TO-IMPLEMENTATION-LANGUAGE \\
+& R-107-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-UML \\
+& R-108-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-XML-SCHEMA \\
+& R-109-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-OCL \\
+& R-110-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-SPARQL \\
+& R-111-BASIC-USE-CASES-COVERED-BY-CONSTRAINT-LANGUAGE \\
+& R-113-INTERACTION-OF-VALIDATION-WITH-REASONING \\
+& R-115-CLOSED-WORLD-ASSUMPTION-CWA \\
+& R-116-UNIQUE-NAME-ASSUMPTION-UNA \\
+& R-117-CONTEXT-SENSITIVE-CONSTRAINTS \\
+& R-118-NAMESPACE-SENSITIVE-CONSTRAINTS \\
+& R-122-TRADE-OFF-BETWEEN-DIMENSIONS-EXPRESSIVITY-COMPLEXITY-PREDICTABILITY \\
+& R-124-DESCRIBE-DATA \\
 \hr
@@
 \subsection{RDF Validation Requirements Not Covered by OWL 2 QL}
+
+Table~\ref{tab:RequirementsNotCoveredOWL2QL-1}
+Table~\ref{tab:RequirementsNotCoveredOWL2QL-2}
+Table~\ref{tab:RequirementsNotCoveredOWL2QL-3}
 
@@
 \hr
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
@@
 
+\section{Conclusion and Future Work}
+
+\section{Appendix}
+
+\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
+
+\textbf{Subclass Expressions}
+
+\begin{ex}
+subClassExpression :=
+    Class |
+    subObjectSomeValuesFrom | DataSomeValuesFrom
+subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
+\end{ex}
+
+\textbf{Superclass Expressions}
+
+\begin{ex}
+superClassExpression :=
+    Class |
+    superObjectIntersectionOf | superObjectComplementOf |
+    superObjectSomeValuesFrom | DataSomeValuesFrom
+\end{ex}
+
+\subsection{Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item subclass axioms (SubClassOf)
+  \item class expression equivalence (EquivalentClasses)
+  \item class expression disjointness (DisjointClasses)
+  \item inverse object properties (InverseObjectProperties)
+  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
+  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
+  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
+  \item property range (ObjectPropertyRange and DataPropertyRange)
+  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
+  \item symmetric properties (SymmetricObjectProperty)
+  \item reflexive properties (ReflexiveObjectProperty)
+  \item irreflexive properties (IrreflexiveObjectProperty)
+  \item asymmetric properties (AsymmetricObjectProperty)
+  \item assertions: DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion
+\end{itemize}
+
+\subsection{Not Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
+  \item self-restriction (ObjectHasSelf)
+  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
+  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
+  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
+  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
+  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
+  \item property inclusions (SubObjectPropertyOf) involving property chains
+  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
+  \item transitive properties (TransitiveObjectProperty)
+  \item keys (HasKey)
+  \item individual equality assertions and negative property assertions (SameIndividual, NegativeObjectPropertyAssertion, NegativeDataPropertyAssertion)
+\end{itemize}
+
 \bibliography{literatur}{}

### 2014-09-25 paper/paper1.tex
R-127 - R-159

--- 2014-09-23 paper/paper1.tex
@@
 
+\subsection{RDF-Specific Validation}
+
+requirements:
+
+\begin{itemize}
+	\item R-120-HANDLE-RDF-COLLECTIONS
+\end{itemize}
+
+\subsection{RDF Shapes}
+
+requirements:
+
+\begin{itemize}
+	\item R-125-RDF-SHAPE-CHECKING
+\end{itemize}
+
+\subsection{RDF Validation Results}
+
+requirements:
+
+\begin{itemize}
+	\item R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS
+	\item R-151-USEFUL-MESSAGE-VALIDATION-RESULTS
+	\item R-152-FIND-NOT-VALIDATED-TRIPLES
+	\item R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS
+	\item R-154-HANDLE-CONSTRAINT-VIOLATIONS
+	\item R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA
+	\item R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS
+	\item R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS
+	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
+	\item R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS
+\end{itemize}
+
 \section{Related Work}
@@
 & R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
+& R-93-DIFFERENCE-BETWEEN-CONSTRAINTS-ON-OBJECT-AND-DATA-PROPERTIES \\
+& R-94-POSITIVE-OBJECT-PROPERTY-ASSERTIONS (ObjectPropertyAssertion) \\
+& R-95-POSITIVE-DATA-PROPERTY-ASSERTIONS (DataPropertyAssertion) \\
+& R-99-STABLE-IDENTIFICATION-OF-CONSTRAINTS \\
+& R-100-SUBSUMPTION (SubClassOf) \\
+& R-101-DECLARATIVE-CONSTRAINT-LANGUAGE \\
+& R-102-INTUITIVE-CONSTRAINT-LANGUAGE \\
+& R-103-HIGH-LEVEL-CONSTRAINT-LANGUAGE \\
+& R-104-CONSTRAINT-LANGUAGE-HAVING-IMPLEMENTATION-LANGUAGE \\
+& R-105-CONSTRAINT-LANGUAGE-TRANSLATABLE-TO-IMPLEMENTATION-LANGUAGE \\
+& R-107-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-UML \\
+& R-108-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-XML-SCHEMA \\
+& R-109-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-OCL \\
+& R-110-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-SPARQL \\
+& R-111-BASIC-USE-CASES-COVERED-BY-CONSTRAINT-LANGUAGE \\
+& R-113-INTERACTION-OF-VALIDATION-WITH-REASONING \\
+& R-115-CLOSED-WORLD-ASSUMPTION-CWA \\
+& R-116-UNIQUE-NAME-ASSUMPTION-UNA \\
+& R-117-CONTEXT-SENSITIVE-CONSTRAINTS \\
+& R-118-NAMESPACE-SENSITIVE-CONSTRAINTS \\
+& R-122-TRADE-OFF-BETWEEN-DIMENSIONS-EXPRESSIVITY-COMPLEXITY-PREDICTABILITY \\
+& R-124-DESCRIBE-DATA \\
+& R-126-CUSTOMIZABLE-VALIDATION-PROCESS \\
+& R-128-HUMAN-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-129-MACHINE-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATION-CONSTRAINTS \\
+& R-130-CONCISE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-131-OWL-AS-CONCRETE-SYNTAX-FORMULATING-CONSTRAINTS \\
+& R-132-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-133-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-DATA \\
+& R-136-MODULARITY-OF-CONSTRAINT-DEFINITIONS \\
+& R-137-LEVERAGE-ON-EXISTING-TECHNOLOGIES \\
+& R-138-CONSTRAINT-LANGUAGE-COMPATIBLE-WITH-SPARQL \\
+& R-139-CONSTRAINT-LANGUAGE-DRIVES-USER-INTERFACE-FORM-GENERATION-AND-PRESENTATION \\
+& R-140-SEPARATE-ONTOLOGIES-FROM-VALIDATION-SCHEMAS \\
+& R-143-CONDITIONAL-TYPED-VALIDATION \\
+& R-147-DISTRIBUTION-OF-CONSTRAINT-SCHEMAS \\
+& R-148-DISTRIBUTED-VALIDATION-IN-COLLABORATIVE-ENVIRONMENTS \\
+& R-149-MANAGEMENT-OF-CONSTRAINT-SCHEMA-EVOLUTION \\
 \hr
@@
 \hr
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
+R-134-SPECIFY-USAGE-OF-TERMS & \\
+R-135-CONSTRAINT-LEVELS & \\
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
 R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
+R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
 \hr
@@
 \end{table}
+
+\section{Conclusion and Future Work}
+
+\section{Appendix}
+
+\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
+
+\textbf{Subclass Expressions}
+
+\begin{ex}
+subClassExpression :=
+    Class |
+    subObjectSomeValuesFrom | DataSomeValuesFrom
+subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
+\end{ex}
+
+\textbf{Superclass Expressions}
+
+\begin{ex}
+superClassExpression :=
+    Class |
+    superObjectIntersectionOf | superObjectComplementOf |
+    superObjectSomeValuesFrom | DataSomeValuesFrom
+\end{ex}
+
+\subsection{Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item subclass axioms (SubClassOf)
+  \item class expression equivalence (EquivalentClasses)
+  \item class expression disjointness (DisjointClasses)
+  \item inverse object properties (InverseObjectProperties)
+  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
+  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
+  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
+  \item property range (ObjectPropertyRange and DataPropertyRange)
+  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
+  \item symmetric properties (SymmetricObjectProperty)
+  \item reflexive properties (ReflexiveObjectProperty)
+  \item irreflexive properties (IrreflexiveObjectProperty)
+  \item asymmetric properties (AsymmetricObjectProperty)
+  \item assertions: DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion
+\end{itemize}
+
+\subsection{Not Supported Constructs in OWL 2 QL}
+
+\begin{itemize}
+	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
+  \item self-restriction (ObjectHasSelf)
+  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
+  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
+  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
+  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
+  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
+  \item property inclusions (SubObjectPropertyOf) involving property chains
+  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
+  \item transitive properties (TransitiveObjectProperty)
+  \item keys (HasKey)
+  \item individual equality assertions and negative property assertions (SameIndividual, NegativeObjectPropertyAssertion, NegativeDataPropertyAssertion)
+\end{itemize}
 

### 2014-09-25 paper/paper1.tex
R-160 - R-182

--- 2014-09-23 paper/paper1.tex
@@
 & R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
+& R-93-DIFFERENCE-BETWEEN-CONSTRAINTS-ON-OBJECT-AND-DATA-PROPERTIES \\
+& R-94-POSITIVE-OBJECT-PROPERTY-ASSERTIONS (ObjectPropertyAssertion) \\
+& R-95-POSITIVE-DATA-PROPERTY-ASSERTIONS (DataPropertyAssertion) \\
+& R-99-STABLE-IDENTIFICATION-OF-CONSTRAINTS \\
+& R-100-SUBSUMPTION (SubClassOf) \\
+& R-101-DECLARATIVE-CONSTRAINT-LANGUAGE \\
+& R-102-INTUITIVE-CONSTRAINT-LANGUAGE \\
+& R-103-HIGH-LEVEL-CONSTRAINT-LANGUAGE \\
+& R-104-CONSTRAINT-LANGUAGE-HAVING-IMPLEMENTATION-LANGUAGE \\
+& R-105-CONSTRAINT-LANGUAGE-TRANSLATABLE-TO-IMPLEMENTATION-LANGUAGE \\
+& R-107-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-UML \\
+& R-108-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-XML-SCHEMA \\
+& R-109-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-OCL \\
+& R-110-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-SPARQL \\
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Covered by OWL 2 QL}
+\label{tab:RequirementsCoveredOWL2QL}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+& R-111-BASIC-USE-CASES-COVERED-BY-CONSTRAINT-LANGUAGE \\
+& R-113-INTERACTION-OF-VALIDATION-WITH-REASONING \\
+& R-115-CLOSED-WORLD-ASSUMPTION-CWA \\
+& R-116-UNIQUE-NAME-ASSUMPTION-UNA \\
+& R-117-CONTEXT-SENSITIVE-CONSTRAINTS \\
+& R-118-NAMESPACE-SENSITIVE-CONSTRAINTS \\
+& R-122-TRADE-OFF-BETWEEN-DIMENSIONS-EXPRESSIVITY-COMPLEXITY-PREDICTABILITY \\
+& R-124-DESCRIBE-DATA \\
+& R-126-CUSTOMIZABLE-VALIDATION-PROCESS \\
+& R-128-HUMAN-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-129-MACHINE-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATION-CONSTRAINTS \\
+& R-130-CONCISE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-131-OWL-AS-CONCRETE-SYNTAX-FORMULATING-CONSTRAINTS \\
+& R-132-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
+& R-133-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-DATA \\
+& R-136-MODULARITY-OF-CONSTRAINT-DEFINITIONS \\
+& R-137-LEVERAGE-ON-EXISTING-TECHNOLOGIES \\
+& R-138-CONSTRAINT-LANGUAGE-COMPATIBLE-WITH-SPARQL \\
+& R-139-CONSTRAINT-LANGUAGE-DRIVES-USER-INTERFACE-FORM-GENERATION-AND-PRESENTATION \\
+& R-140-SEPARATE-ONTOLOGIES-FROM-VALIDATION-SCHEMAS \\
+& R-143-CONDITIONAL-TYPED-VALIDATION \\
+& R-147-DISTRIBUTION-OF-CONSTRAINT-SCHEMAS \\
+& R-148-DISTRIBUTED-VALIDATION-IN-COLLABORATIVE-ENVIRONMENTS \\
+& R-149-MANAGEMENT-OF-CONSTRAINT-SCHEMA-EVOLUTION \\
+& R-160-OPEN-SOURCE-CONSTRAINT-VALIDATION \\
+& R-161-ACCEPTABLE-PERFORMANCE-OF-VALIDATION-ALGORITHM \\
+& R-162-SPECIFICATION-PUBLICLY-AVAILABLE \\
+& R-163-IMPLEMENTATION-EXISTS \\
+& R-164-IMPLEMENTATION-PUBLICLY-AVAILABLE \\
+& R-165-EXECUTABLE-DEMOS-EXAMPLES-USE-CASES \\
+& R-168-PERFORM-BIG-DATASETS \\
+& R-169-RDF-REPRESENTATION-OF-CONSTRAINT-LANGUAGE \\
+& R-173-SEPARATE-CONSTRAINTS-FROM-VOCABULARIES-AND-ONTOLOGIES \\
+& R-174-REUSE-CONSTRAINTS \\
+& R-175-DISCOVER-CONSTRAINTS \\
+& R-177-DEFINE-SEMANTICS-FOR-CONSTRAINTS \\
+& R-178-ASSOCIATE-CONSTRAINTS-WITH-VOCABULARIES \\
+& R-182-USE-KNOWN-CONCRETE-SYNTAX \\
 \hr
@@
 R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
+R-134-SPECIFY-USAGE-OF-TERMS & \\
+R-135-CONSTRAINT-LEVELS & \\
 R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
 R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
+R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
+R-166-RDF-STREAMING-VALIDATION & \\
+R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
+R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
+R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
+R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
+R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
+R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
+R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
+R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
 \hr

### 2014-09-25 paper/paper1.tex
R-183 - R-199

@@
 	\item R-43-COMPARISONS-BASED-ON-DATATYPE
+	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
 \end{itemize}
@@
 & R-182-USE-KNOWN-CONCRETE-SYNTAX \\
+& R-184-COMPACT-CONCRETE-SYNTAX \\
+& R-187-DEFINE-SEMANTICS-OF-CONSTRAINTS-IN-TERMS-OF-SPARQL \\
+& R-190-SPECIFY-EXPECTED-BEHAVIOR-UNDER-ALL-POSSIBLE-ENTAILMENT-REGIMES \\
+& R-192-DEFINE-ANNOTATIONS-FOR-CONSTRAINTS \\
+& R-195-CONSTRAINT-LANGUAGE-EASY-TO-CONSUME-BY-TOOLS \\
+& R-197-ATTACH-CONSTRAINTS-TO-CLASSES \\
+& R-198-RDF-VALIDATION-AFTER-INFERENCING \\
+& R-199-RDF-VALIDATION-MUST-COMPILE-DOWN-TO-SPARQL \\
 \hr
@@
 R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (ObjectUnionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
 R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
@@
 R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
+R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
+R-185-FEDERALIZED-RDF-VALIDATION & \\
+R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
+R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
+R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
+R-191-SHAPES-RELATED-TO-TYPES & \\
+R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
+R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
 \hr

### 2014-09-25 paper/paper1.tex
R-11 example

@@
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+
+\setcounter{secnumdepth}{5}
 
@@
 
-\textbf{class-specific disjoint data properties}
+\subsubsection{Class-Specific Disjoint Data Properties}
+
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
+
+\begin{itemize}
+	\item exclusive OR of data properties
+	\item with OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
+\end{itemize}
 
@@
 
-\textbf{class-specific disjoint object properties}
+valid data (ShEx):
 
-\textbf{Class-Specific Disjoint Group of Properties}
+\begin{ex}
+<Anakin>
+    foaf:name "Anakin Skywalker" ;
+		foaf:familyName "Skywalker" .
+\end{ex}
 
-requirements DB:
-\begin{itemize}
-  \item ID: R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-	\item URL: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/20}
-\end{itemize}
+\begin{ex}
+<Anakin>
+    foaf:givenName "Anakin" ;
+		foaf:givenName "Darth" ;
+    foaf:familyName "Skywalker" .
+\end{ex}
+
+invalid data (ShEx):
+
+\begin{ex}
+<Anakin>
+    foaf:name "Anakin Skywalker" ;
+    foaf:givenName "Anakin" ;
+    foaf:familyName "Skywalker" .
+\end{ex}
+
+\subsubsection{Class-Specific Disjoint Object Properties}
+
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC
+
+\subsubsection{Class-Specific Disjoint Group of Properties}
+
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
 

### 2014-09-25 paper/paper1.tex
Membership in Controlled Vocabularies

@@
 
+\begin{itemize}
+	\item exclusive OR of property groups
+	\item with OWL 2, inclusive OR of property groups would be possible to express, but not exclusive OR of property groups
+\end{itemize}
+
 A \textless Human\textgreater has either a name or at least 1 given name and 1 family name.
@@
 \end{itemize}
+
+constraint (DSP):
+
+\begin{ex}
+:bookDescriptionTemplate 
+    a dsp:DescriptionTemplate ;
+    dsp:resourceClass swrc:Book ; 
+    dsp:statementTemplate [
+        a dsp:NonLiteralStatementTemplate ;
+        dsp:property dcterms:subject ; 
+        dsp:nonLiteralConstraint [ 
+            a dsp:NonLiteralConstraint ;
+            dsp:valueClass skos:Concept ; 
+            dsp:vocabularyEncodingScheme :BookSubjects, :BookTopics, :BookCategories ] ] .
+\end{ex}
+
+A DSP consists of \ms{dsp:DescriptionTemplate}s that put constraints on instances of a certain class (\ms{dsp:resourceClass}). 
+\ms{:bookDescriptionTemplate} describes resources of the type \ms{swrc:Book}.
+The constraints can either be constraints on the description itself, e.g.
+a minimum occurrence of instances of this class.
+Additionally, constraints on single properties can be defined within a \ms{dsp:StatementTemplate}.
+The \ms{dsp:NonLiteralStatementTemplate} restricts books to have \ms{dcterms:subject} (\ms{dsp:property}) relationships to RDF objects which are further described by the \ms{dsp:NonLiteralConstraint}.
+These RDF objects have to be of the class \ms{skos:Concept} (\ms{dsp:ValueClass}).
+Controlled vocabularies (like \ms{:BookSubjects}) are represented as \ms{skos:ConceptSchemes} in RDF and as \ms{dsp:VocabularyEncodingScheme}s in DSP.
+\ms{dsp:VocabularyEncodingScheme} points to a list of controlled vocabularies the \ms{skos:Concept} resources must be members of.
+The controlled vocabulary members (\ms{skos:Concept}s) are related to the controlled vocabulary (\ms{skos:ConceptScheme}) via the object properties \ms{skos:inScheme} and \ms{dcam:memberOf}.
+
+valid data (DSP):
+
+\begin{ex}
+:ArtficialIntelligence
+    a swrc:Book ;
+    dcterms:subject :ComputerScience .
+:ComputerScience
+    a skos:Concept ;
+    dcam:memberOf :BookSubjects ;
+    skos:inScheme :BookSubjects .
+:BookSubjects
+    a skos:ConceptScheme .
+\end{ex}
+
+invalid data (DSP):
+
+\begin{ex}
+:ArtficialIntelligence
+    a swrc:Book ;
+    dcterms:subject :ComputerScience .
+:ComputerScience
+    a skos:Concept ;
+    dcam:memberOf :BooksAboutBirds ;
+    skos:inScheme :BooksAboutBirds ;
+    dcam:memberOf :BookSubjects ;
+    skos:inScheme :BookSubjects .
+:BookSubjects
+    a skos:ConceptScheme .
+\end{ex}
+
+The related subject (\ms{:ComputerScience}) is a member of a controlled vocabulary (\ms{:BooksAboutBirds}) 
+which is not part of the list of allowed controlled vocabularies.
 
@@
 \end{itemize}
+
+\subsection{Requirements Covered by OWL 2 DL But Not by OWL 2 QL}
 

### 2014-09-26 paper/paper1.tex
R-44-PATTERN-MATCHING-ON-RDF-LITERALS

@@
 
+\subsubsection{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}
+
+constraints (OWL 2 DL) [description logics abstract syntax]:
+
+\begin{ex}
+ToDO
+\end{ex}
+
+constraints (OWL 2 DL) [functional-style syntax]:
+
+\begin{ex}
+Declaration( Datatype( :SSN ) ) 
+DatatypeDefinition( 
+    :SSN
+    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
+DataPropertyRange( :hasSSN :SSN ) 
+\end{ex}
+
+constraints (OWL 2 DL) [turtle syntax]:
+
+\begin{ex}
+:SSN 
+    a rdfs:Datatype ;
+    owl:equivalentClass [
+        a rdfs:Datatype ;
+        owl:onDatatype xsd:string ;
+        owl:withRestrictions ( 
+            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
+\end{ex}
+
+\begin{itemize}
+	\item OWL 2 construct 'DatatypeRestriction' not allowed for OWL 2 QL
+\end{itemize}
+
+valida data (OWL 2 DL):
+
+\begin{ex}
+:IimBernersLee
+    :hasSSN "123-45-6789"^^:SSN .
+\end{ex}
+
+invalida data (OWL 2 DL):
+
+\begin{ex}
+:IimBernersLee
+    :hasSSN "123456789"^^:SSN .
+\end{ex}
+
 \subsection{Calculations on and Comparisons of RDF Literals}
@@
 \begin{itemize}
+	\item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
 	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
-  \item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
 	\item R-46-CONSTRAINING-FACETS
 	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
+	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
 \end{itemize}

### 2014-09-26 paper/paper1.tex
R-44-PATTERN-MATCHING-ON-RDF-LITERALS

@@
 \end{itemize}
+
+A social security number is a string that matches the given regular expression. 
+The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
+The first axiom explicitly declares :SSN to be a datatype. 
+The datatype :SSN can be used just like any other datatype; 
+for example, it is used in the third axiom to define the range of the :hasSSN property.
 

### 2014-09-26 paper/paper1.tex
R-45-RANGES-OF-RDF-LITERAL-VALUES

@@
 \end{itemize}
+
+\subsubsection{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}
+
+\begin{itemize}
+	\item see 'Pattern Matching'
+\end{itemize}
+
+\subsubsection{R-45-RANGES-OF-RDF-LITERAL-VALUES}
+
+constraints (OWL 2 DL) [description logics abstract syntax]:
+
+\begin{ex}
+ToDO
+\end{ex}
+
+constraints (OWL 2 DL) [functional-style syntax]:
+
+\begin{ex}
+Declaration( Datatype( :NumberPlayersPerWorldCupTeam ) ) 
+DatatypeDefinition( 
+    :NumberPlayersPerWorldCupTeam
+    DatatypeRestriction( 
+        xsd:nonNegativeInteger 
+        xsd:minInclusive "1"^^xsd:nonNegativeInteger 
+        xsd:maxInclusive "23"^^xsd:nonNegativeInteger ) )     
+DataPropertyRange( :position :NumberPlayersPerWorldCupTeam ) 
+\end{ex}
+
+constraints (OWL 2 DL) [turtle syntax]:
+
+\begin{ex}
+:NumberPlayersPerWorldCupTeam
+    a rdfs:Datatype ;
+    owl:equivalentClass [
+        a rdfs:Datatype ;
+        owl:onDatatype xsd:nonNegativeInteger ;
+        owl:withRestrictions ( 
+            [ xsd:minInclusive "1"^^xsd:nonNegativeInteger ]
+            [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
+\end{ex}
+
+The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most.
+
+valida data (OWL 2 DL):
+
+\begin{ex}
+:MarioGoetze
+    :position "19"^^:NumberPlayersPerWorldCupTeam .
+\end{ex}
+
+invalida data (OWL 2 DL):
+
+\begin{ex}
+:MarioGoetze
+    :position "99"^^:NumberPlayersPerWorldCupTeam .
+\end{ex}
 

### 2014-09-26 paper/paper1.tex
R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-

@@
 
-valida data (OWL 2 DL):
+valid data (OWL 2 DL):
 
@@
 
-invalida data (OWL 2 DL):
+invalid data (OWL 2 DL):
 
@@
 \end{itemize}
+
+\subsubsection{R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}
+
+constraints (DQTP):
+
+ONELANGPattern \cite{Kontokostas2014}
+
+A literal value should contain at most
+1 literal for a language. P1 is the property containing the
+literal and V1 is the language we want to check.
+
+\begin{ex}
+SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
+    BIND ( lang(?c) AS ?l )
+    FILTER (isLiteral (?c) && lang(?c) = %%V1%%)}
+GROUP BY ?s HAVING COUNT (?l) > 1
+\end{ex}
+
+test binding (DQTP):
+
+a single English (“en”) foaf:name
+
+\begin{ex}
+P1 => foaf:name
+V1 => en
+\end{ex}
+
+valid data (DQTP):
+
+\begin{ex}
+:LeiaSkywalker
+    foaf:name 'Leia Skywalker'@en .
+\end{ex}
+
+invalid data (DQTP):
+
+\begin{ex}
+:LeiaSkywalker
+    foaf:name 'Leia Skywalker'@en ;
+    foaf:name 'Leia'@en .
+\end{ex}
 

### 2014-09-26 paper/paper1.tex
R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
default values

@@
 \end{itemize}
+
+\subsubsection{R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}
+
+\begin{itemize}
+	\item see R-38-DEFAULT-VALUES-OF-RDF-LITERALS
+\end{itemize}
+
+\subsubsection{R-38-DEFAULT-VALUES-OF-RDF-LITERALS}
+
+rule (SPIN):
+
+Jedis have only 1 blue laser sword per default.
+Siths, in contrast, normally have 2 red laser swords.
+
+\begin{ex}
+owl:Thing
+    spin:rule [
+        a sp:Construct ;
+            sp:text """
+                CONSTRUCT {            
+                    ?this :laserSwordColor "blue"^^xsd:string ;
+                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
+                }
+                WHERE {             
+                    ?this a :Jedi .            
+                } """ ; ] .
+owl:Thing
+    spin:rule [
+        a sp:Construct ;
+            sp:text """
+                CONSTRUCT {
+                    ?this :laserSwordColor "red"^^xsd:string ;
+                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
+                }
+                WHERE {             
+                    ?this a :Sith .            
+                } """ ; ] .
+\end{ex}
+
+data (SPIN):
+
+\begin{ex}
+:Joda a :Jedi .
+:DarthSidious a :Sith .
+\end{ex}
+
+inferred triples (SPIN):
+
+\begin{ex}
+:Joda 
+    :laserSwordColor "blue"^^xsd:string ;
+    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
+:DarthSidious 
+    :laserSwordColor "red"^^xsd:string ;
+    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
+\end{ex}
 

### 2014-09-27 paper/paper1.tex
R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS

@@
 R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC
+
+\begin{itemize}
+	\item see R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
+\end{itemize}
 
@@
 
+Covering approaches:
+
+DQTP (MATCH Pattern), OWL 2 DL, RS, ShEx, SPARQL, SPIN
+
 constraints (OWL 2 DL) [description logics abstract syntax]:
@@
 \begin{ex}
-ToDO
+
 \end{ex}
@@
 
+\subsubsection{R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS}
+
+Covering approaches: DQTP (MATCH Pattern), OWL 2 DL, SPARQL, SPIN
+
+constraints (DQTP):
+
+MATCH Pattern \cite{Kontokostas2014}
+
+Application logic or real world constraints may put restrictions on the form of a literal value.
+P1 is the property we need to check against REGEX and
+NOP can be a not operator (!) or empty.
+
+\begin{ex}
+SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
+    FILTER ( %%NOP%% regex(str(?value), %%REGEX%) ) }
+\end{ex}
+
+example test bindings (DQTP):
+
+\begin{ex}
+1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
+2. dbo:postCode format is different ‘!’ from 'ˆ[0-9]{5}$'
+3. foaf:phone contains any letters ('[A-Za-z]')
+\end{ex}
+
+test binding (DQTP):
+
+\begin{ex}
+dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
+
+P1 => dbo:isbn
+NOP => !
+REGEX => 'ˆ([iIsSbBnN 0-9-])*$'
+\end{ex}
+
+valid data (DQTP):
+
+\begin{ex}
+:FoundationsOfSWTechnologies
+    dbo:isbn 'ISBN-13 978-1420090505' .
+\end{ex}
+
+invalid data (DQTP):
+
+\begin{ex}
+:HandbookOfSWTechnologies
+    dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
+\end{ex}
+
 \subsection{Calculations on and Comparisons of RDF Literals}
@@
 \subsection{Constraining Facets on RDF Literals}
+
+XSD constraining facets: \url{http://www.w3.org/TR/2001/REC-xmlschema-2-20010502/#rf-facets}
 
@@
 R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
 R-41-STATISTICAL-COMPUTATIONS & SPIN \\
@@
 R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
 R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\

### 2014-09-27 paper/paper1.tex
R-120-HANDLE-RDF-COLLECTIONS

@@
 \end{itemize}
+
+examples:
+
+\begin{itemize}
+	\item size of collection
+	\item first / last element of list must be a specific RDF literal
+	\item compare elements of collection
+	\item are collections identical?
+	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
+	\item 2. list element equals ''
+	\item Does the list have more than 10 elements?
+\end{itemize}
+
+constraint (SPIN):
+
+retrieves the 2. item from the list (2. student of Jedi mentor Jinn)
+
+function call (SPIN):
+
+\begin{ex}
+BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
+\end{ex}
+
+function (SPIN):
+
+\begin{ex}
+:getListItem
+    a spin:Function ; rdfs:subClassOf spin:Functions ;
+    spin:constraint [
+        rdf:type spl:Argument ;
+        spl:predicate sp:arg1 ;
+        spl:valueType rdf:List ;
+        rdfs:comment "list" ; ] ;
+    spin:constraint [
+        rdf:type spl:Argument ;
+        spl:predicate sp:arg2 ;
+        spl:valueType xsd:nonNegativeInteger ;
+        rdfs:comment "item position (starting with 0)" ; ] ;
+    spin:body [
+        a sp:SELECT ;
+        sp:text """
+            SELECT ?item
+            WHERE {
+                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
+    spin:returnType rdfs:Resource .
+\end{ex}
+
+data:
+
+\begin{ex}
+:Jinn :students 
+     ( :Xanatos :Kenobi ) . 
+\end{ex}
+
+result:
+
+\begin{ex}
+:Kenobi
+\end{ex}
 

### 2014-09-27 paper/paper1.tex
R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS

@@
 \end{itemize}
+
+\subsubsection{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS}
+
+\begin{itemize}
+	\item see R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
+	\item covering approaches: ShEx, SPIN
+\end{itemize}
+
+\subsubsection{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}
+
+\begin{itemize}
+	\item instances of specific class must not have some object property
+  \item OWL 2 DL: ObjectComplementOf ( DataSomeValuesFrom ( DataPropertyExpression rdfs:Literal ) )
+	\item covering approaches: ShEx, SPIN
+\end{itemize}
+
+constraint (SPIN)
+
+A matching triple has any predicate except those excluded by the '-' operator.
+
+A matching triple has any object except those excluded by the '-' operator.
+
+\begin{ex}
+
+\end{ex}
 

### 2014-09-28 paper/paper1.tex
R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS

@@
 \begin{itemize}
-	\item see R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
+	\item instances of specific class must not have some object property
+  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
 	\item covering approaches: ShEx, SPIN
@@
 
+constraint (SPIN)
+
+A matching triple has any predicate except those excluded by the '-' operator.
+
+constraint (ShEx):
+
+\begin{ex}
+<FeelingForce> {
+    :feelingForce 'true'^^xsd:boolean ,
+    :attitute xsd:string }
+<JediMentor> {
+    :feelingForce 'true'^^xsd:boolean ,
+    :attitute 'good'^^xsd:string ,
+    :laserSwordColor xsd:string ,
+    :numberLaserSwords xsd:nonNegativeInteger ,
+    :mentorOf @<JediStudent> ,
+    - :studentOf @<JediMentor> }
+<JediStudent> {
+    :feelingForce 'true'^^xsd:boolean ,
+    :attitute 'good'^^xsd:string ,
+    :laserSwordColor xsd:string ,
+    :numberLaserSwords xsd:nonNegativeInteger ,
+    - :mentorOf @<JediStudent> ,
+    :studentOf @<JediMentor> }
+\end{ex}
+
+individuals matching 'FeelingForce' and 'JediMentor' data shapes:
+
+\begin{ex}
+:Obi-Wan 
+    :feelingForce 'true'^^xsd:boolean ;
+    :attitute 'good'^^xsd:string ;
+    :laserSwordColor 'blue'^^xsd:string ,
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
+    :mentorOf :Anakin .
+\end{ex}
+
+individuals matching 'FeelingForce' and 'JediStudent' data shapes:
+
+\begin{ex}
+:Anakin 
+    :feelingForce 'true'^^xsd:boolean ;
+    :attitute 'good'^^xsd:string ;
+    :laserSwordColor 'blue'^^xsd:string ,
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
+    :studentOf :Obi-Wan . 
+\end{ex}
+
 \subsubsection{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}
@@
 \begin{itemize}
-	\item instances of specific class must not have some object property
-  \item OWL 2 DL: ObjectComplementOf ( DataSomeValuesFrom ( DataPropertyExpression rdfs:Literal ) )
+	\item analogous to R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
 	\item covering approaches: ShEx, SPIN
 \end{itemize}
-
-constraint (SPIN)
-
-A matching triple has any predicate except those excluded by the '-' operator.
-
-A matching triple has any object except those excluded by the '-' operator.
-
-\begin{ex}
-
-\end{ex}
 

### 2014-09-28 paper/paper1.tex
R-200-NEGATIVE-LITERAL-CONSTRAINTS

@@
 \begin{itemize}
-	\item for which RDF validation requirement the expressivity of DL-LiteA respectively OWL 2 QL is sufficient?
-	\item for which RDF validation requirement additional constraint languages are needed?
+	\item for which RDF validation requirements the expressivity of DL-Lite$_A$ respectively OWL 2 QL is sufficient?
+	\item for which RDF validation requirements additional constraint languages are needed?
 	\item which constraint languages are suitable to express remaining requirements?
@@
 \begin{ex}
-(foaf:name xsd:string  | foaf:givenName xsd:string+, foaf:familyName xsd:string)
-\end{ex}
-
-valid data (ShEx):
-
-\begin{ex}
-<Anakin>
-    foaf:name "Anakin Skywalker" ;
-		foaf:familyName "Skywalker" .
-\end{ex}
-
-\begin{ex}
-<Anakin>
+<Human> { (  
+    foaf:name xsd:string | foaf:givenName xsd:string+ , 
+    foaf:familyName xsd:string ) }
+\end{ex}
+
+Individuals matching the 'Human' data shape:
+
+\begin{ex}
+:Han
+    foaf:name "Han Solo" ;
+    foaf:familyName "Solo" .
+:Anakin
     foaf:givenName "Anakin" ;
@@
 
-invalid data (ShEx):
-
-\begin{ex}
-<Anakin>
+Individual not matching the 'Human' data shape:
+
+\begin{ex}
+:Anakin
     foaf:name "Anakin Skywalker" ;
@@
 
+constraint (ShEx):
+
 A \textless Human\textgreater has either a name or at least 1 given name and 1 family name.
-
-constraint (ShEx):
 
@@
         |                                   
-            foaf:givenName xsd:string+,      
+            foaf:givenName xsd:string+ ,      
             foaf:familyName xsd:string
@@
 
-valid data (ShEx):
-
-\begin{ex}
-<Anakin>
+Individuals matching the 'Human' data shape:
+
+\begin{ex}
+:Anakin
     foaf:givenName "Anakin" ;
@@
 \begin{ex}
-<Anakin>
+:Anakin
     foaf:name "Anakin Skywalker" .
@@
 
-invalid data (ShEx):
-
-\begin{ex}
-<Anakin>
+Individual not matching the 'Human' data shape:
+
+\begin{ex}
+:Anakin
     foaf:givenName "Anakin" ;
@@
 
-data (SPIN):
+data:
 
@@
 
-inferred triples (SPIN):
+inferred triples:
 
@@
     :numberLaserSwords "2"^^xsd:nonNegativeInteger .
+\end{ex}
+
+\subsection{Allowed and Not Allowed Values}
+
+requirements:
+
+\begin{itemize}
+	\item R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS
+  \item R-37-ALLOWED-VALUES-FOR-RDF-LITERALS
+  \item R-33-NEGATIVE-OBJECT-CONSTRAINTS
+	\item R-200-NEGATIVE-LITERAL-CONSTRAINTS
+\end{itemize}
+
+\subsubsection{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS}
+
+\begin{itemize}
+	\item covering approaches:  OWL 2 DL (ObjectOneOf) 
+\end{itemize}
+
+\subsubsection{R-37-ALLOWED-VALUES-FOR-RDF-LITERAL}
+
+\begin{itemize}
+	\item covering approaches:  OWL 2 DL (DataOneOf) 
+\end{itemize}
+
+\subsubsection{R-33-NEGATIVE-OBJECT-CONSTRAINTS}
+
+\begin{itemize}
+	\item covering approaches:  ShEx, SPARQL, SPIN
+	\item analogous to R-200-NEGATIVE-LITERAL-CONSTRAINTS
+\end{itemize}
+
+\subsubsection{R-200-NEGATIVE-LITERAL-CONSTRAINTS}
+
+\begin{itemize}
+	\item definition: A matching triple has any literal except those explicitly excluded
+	\item covering approaches:  ShEx, SPARQL, SPIN
+\end{itemize}
+
+constraint (ShEx):
+
+A matching triple has any literal except those excluded by the '-' operator.
+
+\begin{ex}
+<Jedi> {
+    :feelingForce 'true'^^xsd:boolean ,
+    :attitute 'good'^^xsd:string ,
+    :laserSwordColor 'blue'^^xsd:string ,
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger }
+<Sith> {
+    :feelingForce 'true'^^xsd:boolean ,
+    :attitute - 'good'^^xsd:string ,
+    :laserSwordColor - 'blue'^^xsd:string ,
+    :numberLaserSwords '2'^^xsd:nonNegativeInteger }
+\end{ex}
+
+Individual matching the 'Jedi' data shape:
+
+\begin{ex}
+:Joda 
+    :feelingForce 'true'^^xsd:boolean ;
+    :attitute 'good'^^xsd:string ;
+    :laserSwordColor 'blue'^^xsd:string ,
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
+\end{ex}
+
+Individual matching the 'Sith' data shape:
+
+\begin{ex}
+:DarthSidious
+    :feelingForce 'true'^^xsd:boolean ;
+    :attitute 'evil'^^xsd:string ;
+    :laserSwordColor 'red'^^xsd:string ,
+    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
 \end{ex}
@@
 
-constraint (SPIN)
+constraint (ShEx):
 
 A matching triple has any predicate except those excluded by the '-' operator.
-
-constraint (ShEx):
 
@@
 \end{itemize}
+
+\subsubsection{R-120-HANDLE-RDF-COLLECTIONS}
 
@@
 R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
 R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
@@
 R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
+R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
 \hr

### 2014-09-28 paper/paper1.tex
RDF Validation Requirements Not Covered by OWL 2 QL

@@
 
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
+\label{tab:RequirementsCoveredOWL2DL}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}
+\label{tab:RequirementsCoveredSPIN}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
+\label{tab:RequirementsCoveredShEx}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+
+\hr
+\end{tabular}
+\end{table}
+
+\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
+
+\begin{itemize}
+	\item OWL 2 DL as an instantiation of constraint languages which are high-level, human-friendly, and very expressive 
+\end{itemize}
+
+Table~\ref{tab:RequirementsCoveredOWL2DL}
+
+\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}
+
+\begin{itemize}
+	\item SPIN as an instantiation of constraint languages which are low-level and the most expressive 
+\end{itemize}
+
+Table~\ref{tab:RequirementsCoveredSPIN}
+
+\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
+
+\begin{itemize}
+	\item ShEx as an instantiation of constraint languages which are high-level, human-friendly, intuitive, concise, and less expressive 
+\end{itemize}
+
+Table~\ref{tab:RequirementsCoveredShEx}
+
 \section{Conclusion and Future Work}

### 2014-09-28 paper/paper1.tex
R-43-COMPARISONS-BASED-ON-DATATYPE

@@
 	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
+\end{itemize}
+
+\subsubsection{R-41-STATISTICAL-COMPUTATIONS}
+
+\begin{itemize}
+  \item examples: average, mean, sum
+	\item covering approaches: SPARQL, SPIN
+\end{itemize}
+
+\subsubsection{R-42-COMPUTATIONS-BASED-ON-DATATYPE}
+
+\begin{itemize}
+	\item covering approaches: -
+\end{itemize}
+
+\subsubsection{R-43-COMPARISONS-BASED-ON-DATATYPE}
+
+\begin{itemize}
+	\item covering approaches: DQTP, ShEx, SPARQL, SPIN
+\end{itemize}
+
+constraints (DQTP):
+
+COMP Pattern \cite{Kontokostas2014}
+
+Depending on the property semantics,
+there are cases where two different literal values must have
+a specific ordering with respect to an operator. 
+P1 and P2 are the datatype properties we need to compare and 
+OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=).
+
+\begin{ex}
+SELECT ?s WHERE { 
+    ?s %%P1%% ?v1 .
+    ?s %%P2%% ?v2 .
+    FILTER ( ?v1 %%OP%% ?v2 ) }
+\end{ex}
+
+example bindings (DQTP):
+
+\begin{ex}
+1. dbo:deathDate before ‘<’ dbo:birthDate
+2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
+3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
+\end{ex}
+
+test binding (DQTP):
+
+dbo:deathDate before ‘\textless’ dbo:birthDate
+
+\begin{ex}
+P1 => dbo:deathDate
+P2 => dbo:birthDate
+OP => <
+\end{ex}
+
+valid data:
+
+\begin{ex}
+:AlbertEinstein
+    dbo:birthDate '1879-03-14'^^xsd:date ;
+    dbo:deathDate '1955-04-18'^^xsd:date .
+\end{ex}
+
+invalid data:
+
+\begin{ex}
+:NeilArmstrong
+    dbo:birthDate '2012-08-25'^^xsd:date ;
+    dbo:deathDate '1930-08-05'^^xsd:date .
+\end{ex}
+
+\subsubsection{R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS}
+
+\begin{itemize}
+	\item covering approaches: SPARQL, SPIN
 \end{itemize}
@@
 R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPIN \\
+R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
 R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\

### 2014-09-28 paper/paper1.tex
RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL

@@
 \hr
-Requirements Classification & Requirements \\
-\hr
-
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}
-\label{tab:RequirementsCoveredSPIN}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-
+Requirements Classification (1. level) & Requirements \\
+\hr
+R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) \\
+R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) \\
+R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS (DatatypeDefinition, DatatypeRestriction) \\
+R-46-CONSTRAINING-FACETS (DatatypeDefinition, DatatypeRestriction) \\
+R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) \\
+R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) \\
+R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) \\
+R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) \\
+R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) \\
+R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) \\
+R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) \\
+R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) \\
+R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) \\
+R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) \\
+R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) \\
+R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) \\
+R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) \\
+R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) \\
+R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) \\
+R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) \\
+R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) \\
+R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) \\
+R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) \\
+R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) \\
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS (DatatypeDefinition, DatatypeRestriction) \\
 \hr
@@
 \hr
-
+R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
+R-24-PROVENANCE-CONSTRAINTS & \\
+R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
+R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
+R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
+R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
+R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
+R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
+R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
+R-41-STATISTICAL-COMPUTATIONS & SPIN \\
+R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
+R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
+R-47-LANGUAGE-TAG-MATCHING & SPIN \\
+R-48-MISSING-LANGUAGE-TAGS & SPIN \\
+R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
+R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
+R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
+R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
+R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
+R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
+R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-71-CONDITIONAL-PROPERTIES \\
+R-72-RECOMMENDED-PROPERTIES \\
+R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
+R-134-SPECIFY-USAGE-OF-TERMS & \\
+R-135-CONSTRAINT-LEVELS & \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
+R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
+R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
+R-166-RDF-STREAMING-VALIDATION & \\
+R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
+R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
+R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
+R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
+R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
+R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
+R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
+R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
+R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
+R-185-FEDERALIZED-RDF-VALIDATION & \\
+R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
+R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
+R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
+R-191-SHAPES-RELATED-TO-TYPES & \\
+R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
+R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
+R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
 \hr
@@
 
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
+\label{tab:RequirementsCoveredShEx}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
+R-24-PROVENANCE-CONSTRAINTS & \\
+R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
+R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
+R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
+R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
+R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
+R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
+R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
+R-41-STATISTICAL-COMPUTATIONS & SPIN \\
+R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
+R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
+R-47-LANGUAGE-TAG-MATCHING & SPIN \\
+R-48-MISSING-LANGUAGE-TAGS & SPIN \\
+R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
+R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
+R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
+R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
+R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
+R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
+R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-71-CONDITIONAL-PROPERTIES \\
+R-72-RECOMMENDED-PROPERTIES \\
+R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
+R-134-SPECIFY-USAGE-OF-TERMS & \\
+R-135-CONSTRAINT-LEVELS & \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
+R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
+R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
+R-166-RDF-STREAMING-VALIDATION & \\
+R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
+R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
+R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
+R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
+R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
+R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
+R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
+R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
+R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
+R-185-FEDERALIZED-RDF-VALIDATION & \\
+R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
+R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
+R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
+R-191-SHAPES-RELATED-TO-TYPES & \\
+R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
+R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
+R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Only Covered by SPIN and SPARQL}
+\label{tab:RequirementsCoveredSPIN}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
+R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
+R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
+R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
+R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
+R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
+R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
+R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
+R-24-PROVENANCE-CONSTRAINTS & \\
+R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
+R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
+R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
+R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
+R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
+R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
+R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
+R-41-STATISTICAL-COMPUTATIONS & SPIN \\
+R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
+R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
+R-47-LANGUAGE-TAG-MATCHING & SPIN \\
+R-48-MISSING-LANGUAGE-TAGS & SPIN \\
+R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
+R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
+R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
+R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
+R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
+R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
+R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
+R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
+R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
+R-71-CONDITIONAL-PROPERTIES \\
+R-72-RECOMMENDED-PROPERTIES \\
+R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
+R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
+R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
+R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
+R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
+R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
+R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
+R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
+R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
+R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
+R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
+R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
+R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
+R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
+R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
+R-98-CHECK-VALIDITY-OF-URIS & \\
+R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
+R-112-EXTENSIBLE-CONSTRAINTS & \\
+R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
+R-119-VALIDATION-ON-NAMED-GRAPHS & \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
+R-123-STATE & \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
+R-134-SPECIFY-USAGE-OF-TERMS & \\
+R-135-CONSTRAINT-LEVELS & \\
+R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
+R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
+R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
+R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
+R-166-RDF-STREAMING-VALIDATION & \\
+R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
+R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
+R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
+R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
+R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
+R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
+R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
+R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
+R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
+R-185-FEDERALIZED-RDF-VALIDATION & \\
+R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
+R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
+R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
+R-191-SHAPES-RELATED-TO-TYPES & \\
+R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
+R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
+R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
+\hr
+\end{tabular}
+\end{table}
+
 \subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
@@
 
-\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN}
+\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
+
+\begin{itemize}
+	\item ShEx as an instantiation of constraint languages which are high-level, human-friendly, intuitive, concise, and less expressive 
+\end{itemize}
+
+\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
+
+Table~\ref{tab:RequirementsCoveredShEx}
+
+\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN and SPARQL}
 
@@
 
+\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN and SPARQL}
+\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
+
 Table~\ref{tab:RequirementsCoveredSPIN}
-
-\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
-
-\begin{itemize}
-	\item ShEx as an instantiation of constraint languages which are high-level, human-friendly, intuitive, concise, and less expressive 
-\end{itemize}
-
-Table~\ref{tab:RequirementsCoveredShEx}
 

### 2014-09-29 paper/paper1.tex
validated R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS

@@
 
-A matching triple has any predicate except those excluded by the '-' operator.
+A matching triple has any predicate except those excluded by the '!' operator.
 
@@
 <FeelingForce> {
-    :feelingForce 'true'^^xsd:boolean ,
+    :feelingForce (true) ,
     :attitute xsd:string }
 <JediMentor> {
-    :feelingForce 'true'^^xsd:boolean ,
-    :attitute 'good'^^xsd:string ,
+    :feelingForce (true) ,
+    :attitute ('good') ,
     :laserSwordColor xsd:string ,
@@
     :mentorOf @<JediStudent> ,
-    - :studentOf @<JediMentor> }
+   !:studentOf @<JediMentor> }
 <JediStudent> {
-    :feelingForce 'true'^^xsd:boolean ,
-    :attitute 'good'^^xsd:string ,
+    :feelingForce (true) ,
+    :attitute ('good') ,
     :laserSwordColor xsd:string ,
     :numberLaserSwords xsd:nonNegativeInteger ,
-    - :mentorOf @<JediStudent> ,
+   !:mentorOf @<JediStudent> ,
     :studentOf @<JediMentor> }
@@
 :Obi-Wan 
-    :feelingForce 'true'^^xsd:boolean ;
-    :attitute 'good'^^xsd:string ;
-    :laserSwordColor 'blue'^^xsd:string ,
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
+    :feelingForce true ;
+    :attitute 'good' ;
+    :laserSwordColor 'blue' ;
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
     :mentorOf :Anakin .
@@
 :Anakin 
-    :feelingForce 'true'^^xsd:boolean ;
-    :attitute 'good'^^xsd:string ;
-    :laserSwordColor 'blue'^^xsd:string ,
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ,
+    :feelingForce true ;
+    :attitute 'good' ;
+    :laserSwordColor 'blue' ;
+    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
     :studentOf :Obi-Wan .

### 2014-09-29 paper/paper1.tex
revised R-200-NEGATIVE-LITERAL-CONSTRAINTS example

@@
 
-A matching triple has any literal except those excluded by the '-' operator.
+A matching triple has any literal except those excluded by the '!' operator.
 
@@
 <Jedi> {
-    :feelingForce 'true'^^xsd:boolean ,
-    :attitute 'good'^^xsd:string ,
-    :laserSwordColor 'blue'^^xsd:string ,
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger }
+    :feelingForce (true) ,
+    :attitute ('good') ,
+    :laserSwordColor ('blue') ,
+    :numberLaserSwords ('1'^^xsd:nonNegativeInteger) }
 <Sith> {
-    :feelingForce 'true'^^xsd:boolean ,
-    :attitute - 'good'^^xsd:string ,
-    :laserSwordColor - 'blue'^^xsd:string ,
-    :numberLaserSwords '2'^^xsd:nonNegativeInteger }
+    :feelingForce (true) ,
+    :attitute (!'good') ,
+    :laserSwordColor (!'blue') ,
+    :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
 \end{ex}
@@
 :Joda 
-    :feelingForce 'true'^^xsd:boolean ;
-    :attitute 'good'^^xsd:string ;
-    :laserSwordColor 'blue'^^xsd:string ,
+    :feelingForce (true) ;
+    :attitute ('good') ;
+    :laserSwordColor ('blue') ,
     :numberLaserSwords '1'^^xsd:nonNegativeInteger .
@@
 :DarthSidious
-    :feelingForce 'true'^^xsd:boolean ;
-    :attitute 'evil'^^xsd:string ;
-    :laserSwordColor 'red'^^xsd:string ,
+    :feelingForce (true) ;
+    :attitute ('evil') ;
+    :laserSwordColor ('red') ,
     :numberLaserSwords '2'^^xsd:nonNegativeInteger . 

### 2014-09-30 paper/paper1.tex
R-200-NEGATIVE-LITERAL-CONSTRAINTS

@@
 
+\url{http://w3.org/brief/Mzk2}
+
 \begin{ex}
@@
     :feelingForce (true) ,
-    :attitute (!'good') ,
-    :laserSwordColor (!'blue') ,
+   !:attitute ('good') ,
+   !:laserSwordColor ('blue') ,
     :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
@@
 :Joda 
-    :feelingForce (true) ;
-    :attitute ('good') ;
-    :laserSwordColor ('blue') ,
+    :feelingForce true ;
+    :attitute 'good' ;
+    :laserSwordColor 'blue' ;
     :numberLaserSwords '1'^^xsd:nonNegativeInteger .
@@
 :DarthSidious
-    :feelingForce (true) ;
-    :attitute ('evil') ;
-    :laserSwordColor ('red') ,
+    :feelingForce true ;
+    :attitute 'evil' ;
+    :laserSwordColor 'red' ;
     :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
@@
 A matching triple has any predicate except those excluded by the '!' operator.
+
+\url{http://w3.org/brief/Mzk0}
 

### 2014-09-30 paper/paper1.tex
RDF Validation Requirements Not Covered by OWL 2 But by ShEx

@@
 \begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
+\caption{RDF Validation Requirements Not Covered by OWL 2 But by ShEx}
+\label{tab:RequirementsCoveredShEx}
+\centering
+\begin{tabular}{ll}
+\hr
+Requirements Classification & Requirements \\
+\hr
+R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
+R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
+R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
+R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
+R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
+R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
+R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
+R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
+R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
+R-66-PROPERTY-GROUPS & ShEx, SPIN \\
+R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
+R-125-RDF-SHAPE-CHECKING & ShEx \\
+R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
+R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
+R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
+R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
+R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
+R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
+\hr
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
 \label{tab:RequirementsCoveredShEx}
@@
 \begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
-\label{tab:RequirementsCoveredShEx}
+\caption{RDF Validation Requirements Only Covered by SPIN and SPARQL}
+\label{tab:RequirementsCoveredSPIN}
 \centering
@@
 
-\begin{table}
-\caption{RDF Validation Requirements Only Covered by SPIN and SPARQL}
-\label{tab:RequirementsCoveredSPIN}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-R-24-PROVENANCE-CONSTRAINTS & \\
-R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
-R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
-R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-71-CONDITIONAL-PROPERTIES \\
-R-72-RECOMMENDED-PROPERTIES \\
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
-R-98-CHECK-VALIDITY-OF-URIS & \\
-R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
-R-112-EXTENSIBLE-CONSTRAINTS & \\
-R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
-R-119-VALIDATION-ON-NAMED-GRAPHS & \\
-R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
-R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
-R-123-STATE & \\
-R-125-RDF-SHAPE-CHECKING & ShEx \\
-R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
-R-134-SPECIFY-USAGE-OF-TERMS & \\
-R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
-R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
-R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
-R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
-R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
-R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
-R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
-R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
-R-166-RDF-STREAMING-VALIDATION & \\
-R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
-R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
-R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
-R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
-R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
-R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
-R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
-R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
-R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
-R-185-FEDERALIZED-RDF-VALIDATION & \\
-R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
-R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
-R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
-R-191-SHAPES-RELATED-TO-TYPES & \\
-R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
-R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
-\hr
-\end{tabular}
-\end{table}
-
 \subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}

### 2014-10-03 paper/paper2.tex
presentations
DC 2014 tutorial

@@
 
+\subsection{example validation + inferencing with CWA/UNA}
+
+\begin{ex}
+Let's take an example schema:
+
+  my:IssueShape {
+    x:submitter @my:SubmitterShape
+  }
+  my:SubmitterShape {
+    foaf:name LITERAL
+  }
+
+We can express that as OWL CWA/UNA like so:
+
+  x:submitter a owl:ObjectProperty .
+
+  my:IssueType
+    rdfs:subClassOf
+      [ owl:onProperty x:submitter ;
+        owl:cardinality 1 ] ,
+      [ owl:onProperty x:submitter ;
+        owl:allValuesFrom my:SubmitterType ] .
+
+  foaf:givenName a owl:DatatypeProperty ;
+    rdfs:range xsd:string .
+  foaf:familyName a owl:DatatypeProperty ;
+    rdfs:range xsd:string .
+
+  my:SubmitterType
+    rdfs:subClassOf
+      [ owl:onProperty foaf:givenName ;
+        owl:cardinality 1 ] ,
+      [ owl:onProperty foaf:familyName ;
+        owl:cardinality 1 ] .
+
+A piece of instance data like
+
+  <Issue1> x:submitter _:submitter .
+  _:submitter foaf:givenName "Bob" .
+
+has two untyped nodes. In order to validate, We posit that:
+
+  <Isseu1> a my:IssueType .
+
+and the system then gets to infer that:
+
+  _:submitter a my:SubmitterType .
+
+(Of course, this could have been an anonymous class in the OWL, but I
+gave it a label for clarity here.) CWA validation leads us to believe
+that the foaf:familyName property is missing for _:submitter.
+
+If any arcs are missing from _:submitter other than a type arc, those
+are considered validation errors, but in order to even validate, I
+believe that OWL UNA/CWA (e.g. ICV) is required to do type inferencing
+in order to get anything done. It was this juxtaposition that I was
+trying to point out.
+\end{ex}
+
 \section{Modularize and Separate Semantics and Constraints}
@@
 
+\section{constraints vs. axioms}
+
+see R-201-SEPARATION-OF-CONSTRAINTS-AND-ONTOLOGY-SEMANTICS
+
 \section{Diskussionen}

### 2014-10-04 paper/paper2.tex
separate constraint and axioms

@@
 
+\section{separate constraints and axioms}
+
+\subsection{disjointness}
+
+A disjointness constraint is actually different (both
+semantically and in practice) from the OWL disjointness axiom. I see no
+problem with adding disjointness to an AP where such disjointness is
+needed in the applications that will use the AP (data creation, quality
+control, documentation of your "data set"). In fact, I believe I have
+seen such constraints being used in validation functions that use
+SPARQL, and it doesn't seem to be a problem. As we know (and Tom and I
+will show some examples in Austin), disjointness in the open world can
+be ill-advised precisely because it does not mean the same as
+disjointness in the closed world. In the closed world it may be a common
+requirement; in the open world it can greatly interfere with data
+compatibility. The same is true of cardinality (which has a very
+different meaning in the open world).
+
+I do not see APs as duplicating the OWL axioms -- although the natural
+language terms we use may be the same, the functionality is quite different.
+
+Obviously, this is what we need to keep in mind as we go through our use
+cases. I don't know what problems might arise when we get into the details.
+
 \section{Diskussionen}

### 2014-10-05 paper/paper3.tex
new paper

--- 2014-09-29 paper/paper1.tex
@@
 
-\section{Introduction}
+\section{Idea}
 
-\section{Ideas}
+"What I would consider the greatest success
+for us would be to create something that can be mapped to any reasonable
+validation method, but that makes it easy for people to define the
+constraints they want to use in their application. BIBFRAME has used a
+somewhat reduced DSP in this way: the AP is what drives the BIBFRAME
+instance data editor. (I would love for us to have a similar editor for
+the *creation* of APs.)"
 
-\begin{itemize}
-	\item sind alle constraints abgedeckt?
-	\item kann man alle constraints in SPARQL definieren?
-	\item sind alle constraints mit Logik ausdrückbar?
-	\item vollständig mit Reasoning | OW
-	\item vollständig ohne Reasoning | CW
-	\item es gibt keinen query rewriting mechanismus für OWL 2, nur für OWL-QL
-	\item constraints in einer anderen constraint language definieren wenn constraints nicht in OWL beschrieben werden können
-	\item durch reasoning entstehen Probleme, auf die man nicht gekommen wäre --> sofort nachvollziehbar
-	\item zeigen, dass OWL-QL und constraint language einer konkreten Domäne zusammen vollständig sind
-	\item System entwickeln, das effizient ist / Experimente
-\end{itemize}
+That's interesting!
+Kai and I had a related idea a couple of months ago ;-)
 
------
+There should be 1 constraint language-independent SPIN mapping for each RDF validation constraint (requirement) 
+in order to validate this constraint automatically and independently from any specific constraint language.
 
-Nehmen wir nun an, dass dein Framework welches entsprechende SPARQL Queries generiert diese auf einem SPARQL Endpoint evaluiert der zu der vorliegenden Ontologie bzw.
-des darin verwendeten OWL 2 Profils das entsprechende Entailment Regime realisiert, wären die zurückgegebenen Resultsets vollständig.
-Wie das Entailment Regime im Endpoint realisiert ist, also durch Query Rewriting oder durch Vervollständigung der ABox, ist dabei irrelevant.
+Then, for each constraint language (ShEx, DSP, OWL2) - we want to use in order to express our constraints, 
+we need for each constraint a mapping to the language-independent constraint.
+This way, we do not need a SPIN mapping for each constraint language in order to implement the validation of the language-specific constraint.
+Now, we have immediately an automatic validation of these constraints.
+This way, constraints expressed with different languages can be validated in the same manner without differences.
 
-Wie allerdings bspw. in 
-\url{https://www.uni-ulm.de/fileadmin/website_uni_ulm/iui.inst.090/Lehre/WS_2011-2012/SemWebGrundlagen/LectureNotes.pdf}
-auf Seite 51 veranschaulicht, ist die Komplexität des Reasoning abhängig von der zugrunde gelegten Sprache und kann daher nur in bestimmten Fällen effizient durchgeführt werden.
-Wie in unserem letzten Paper beschrieben zielt unter anderem die Definition von DL-Lite gerade darauf ab Reasoning Aufgaben und Query Answering effizient zu ermöglichen und ist Grundlage des OWL 2 QL Profils.
-Nun ist allgemein bekannt, dass die logische Konsistenz für diese Art von Sprachen effizient geprüft werden kann.
+When we use a UI to define our constraints in a user-friendly way, these constraints can be either mapped to a constraint expressed in a specific constraint language 
+and then to SPIN or directly to SPIN in the background.    
+So, the user does not have to know how to express constraints using a constraint language such as OWL 2, DSP, or ShEx.
 
-Allerding wäre wie bspw. in 
-\url{http://www.aifb.kit.edu/images/d/d2/2005_925_Haase_Consistent_Evol_1.pdf} beschrieben auch eine sogenannte 'User-defined Consistency' denkbar. Genau an dieser Stelle könnten wir ansetzen.
-
-\section{research questions}
-
-\begin{itemize}
-	\item for which RDF validation requirements the expressivity of DL-Lite$_A$ respectively OWL 2 QL is sufficient?
-	\item for which RDF validation requirements additional constraint languages are needed?
-	\item which constraint languages are suitable to express remaining requirements?
-	\item what are the effects of these constraints regarding complexity?
-\end{itemize}
-
-\section{OWL 2 QL}
-
-OWL 2 profiles specification: \cite{owl2profiles2008}
-
-\begin{itemize}
-  \item OWL 2 QL constructs
-	\item Difference between OWL 2 DL and OWL 2 QL
-\end{itemize}
-
-\textbf{Logical Underpinning for OWL 2 QL.}
-OWL 2 QL is based on the DL-Lite family of description logics.
-Several variants of DL-Lite have been described in the literature, and DL-Lite$_R$ provides the logical underpinning for OWL 2 QL.
-DL-Lite$_R$ does not require the unique name assumption (UNA), since making this assumption would have no impact on the semantic consequences of a DL-Lite$_R$ ontology.
-More expressive variants of DL-Lite, such as DL-Lite$_A$, extend DL-Lite$_R$ with functional properties, and these can also be extended with keys; however, for query answering to remain in LOGSPACE, these extensions require UNA and need to impose certain global restrictions on the interaction between properties used in different types of axiom.
-Basing OWL 2 QL on DL-Lite$_R$ avoids practical problems involved in the explicit axiomatization of UNA \cite{owl2profiles2008}.
-
-\section{RDF Validation Requirements Not Covered By OWL 2 QL}
-
-\subsection{Class-Specific Disjointness of Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
-  \item R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC
-  \item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-\end{itemize}
-
-\subsubsection{Class-Specific Disjoint Data Properties}
-
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
-
-\begin{itemize}
-	\item exclusive OR of data properties
-	\item with OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
-\end{itemize}
-
-constraint (ShEx):
-
-\begin{ex}
-<Human> { (  
-    foaf:name xsd:string | foaf:givenName xsd:string+ , 
-    foaf:familyName xsd:string ) }
-\end{ex}
-
-Individuals matching the 'Human' data shape:
-
-\begin{ex}
-:Han
-    foaf:name "Han Solo" ;
-    foaf:familyName "Solo" .
-:Anakin
-    foaf:givenName "Anakin" ;
-    foaf:givenName "Darth" ;
-    foaf:familyName "Skywalker" .
-\end{ex}
-
-Individual not matching the 'Human' data shape:
-
-\begin{ex}
-:Anakin
-    foaf:name "Anakin Skywalker" ;
-    foaf:givenName "Anakin" ;
-    foaf:familyName "Skywalker" .
-\end{ex}
-
-\subsubsection{Class-Specific Disjoint Object Properties}
-
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC
-
-\begin{itemize}
-	\item see R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC
-\end{itemize}
-
-\subsubsection{Class-Specific Disjoint Group of Properties}
-
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-
-\begin{itemize}
-	\item exclusive OR of property groups
-	\item with OWL 2, inclusive OR of property groups would be possible to express, but not exclusive OR of property groups
-\end{itemize}
-
-constraint (ShEx):
-
-A \textless Human\textgreater has either a name or at least 1 given name and 1 family name.
-
-\begin{ex}
-<Human> {                           
-    (                                    
-            foaf:name xsd:string              
-        |                                   
-            foaf:givenName xsd:string+ ,      
-            foaf:familyName xsd:string
-    )
-}
-\end{ex}
-
-Individuals matching the 'Human' data shape:
-
-\begin{ex}
-:Anakin
-    foaf:givenName "Anakin" ;
-    foaf:familyName "Skywalker" .
-\end{ex}
-
-\begin{ex}
-:Anakin
-    foaf:name "Anakin Skywalker" .
-\end{ex}
-
-Individual not matching the 'Human' data shape:
-
-\begin{ex}
-:Anakin
-    foaf:givenName "Anakin" ;
-    foaf:familyName "Skywalker" ;
-    foaf:name "Anakin Skywalker" .
-\end{ex}
-
-\subsection{Default Values}
-
-requirements:
-
-\begin{itemize}
-	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
-  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
-\end{itemize}
-
-\subsubsection{R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}
-
-\begin{itemize}
-	\item see R-38-DEFAULT-VALUES-OF-RDF-LITERALS
-\end{itemize}
-
-\subsubsection{R-38-DEFAULT-VALUES-OF-RDF-LITERALS}
-
-rule (SPIN):
-
-Jedis have only 1 blue laser sword per default.
-Siths, in contrast, normally have 2 red laser swords.
-
-\begin{ex}
-owl:Thing
-    spin:rule [
-        a sp:Construct ;
-            sp:text """
-                CONSTRUCT {            
-                    ?this :laserSwordColor "blue"^^xsd:string ;
-                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
-                }
-                WHERE {             
-                    ?this a :Jedi .            
-                } """ ; ] .
-owl:Thing
-    spin:rule [
-        a sp:Construct ;
-            sp:text """
-                CONSTRUCT {
-                    ?this :laserSwordColor "red"^^xsd:string ;
-                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
-                }
-                WHERE {             
-                    ?this a :Sith .            
-                } """ ; ] .
-\end{ex}
-
-data:
-
-\begin{ex}
-:Joda a :Jedi .
-:DarthSidious a :Sith .
-\end{ex}
-
-inferred triples:
-
-\begin{ex}
-:Joda 
-    :laserSwordColor "blue"^^xsd:string ;
-    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
-:DarthSidious 
-    :laserSwordColor "red"^^xsd:string ;
-    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
-\end{ex}
-
-\subsection{Allowed and Not Allowed Values}
-
-requirements:
-
-\begin{itemize}
-	\item R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS
-  \item R-37-ALLOWED-VALUES-FOR-RDF-LITERALS
-  \item R-33-NEGATIVE-OBJECT-CONSTRAINTS
-	\item R-200-NEGATIVE-LITERAL-CONSTRAINTS
-\end{itemize}
-
-\subsubsection{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS}
-
-\begin{itemize}
-	\item covering approaches:  OWL 2 DL (ObjectOneOf) 
-\end{itemize}
-
-\subsubsection{R-37-ALLOWED-VALUES-FOR-RDF-LITERAL}
-
-\begin{itemize}
-	\item covering approaches:  OWL 2 DL (DataOneOf) 
-\end{itemize}
-
-\subsubsection{R-33-NEGATIVE-OBJECT-CONSTRAINTS}
-
-\begin{itemize}
-	\item covering approaches:  ShEx, SPARQL, SPIN
-	\item analogous to R-200-NEGATIVE-LITERAL-CONSTRAINTS
-\end{itemize}
-
-\subsubsection{R-200-NEGATIVE-LITERAL-CONSTRAINTS}
-
-\begin{itemize}
-	\item definition: A matching triple has any literal except those explicitly excluded
-	\item covering approaches:  ShEx, SPARQL, SPIN
-\end{itemize}
-
-constraint (ShEx):
-
-A matching triple has any literal except those excluded by the '!' operator.
-
-\begin{ex}
-<Jedi> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor ('blue') ,
-    :numberLaserSwords ('1'^^xsd:nonNegativeInteger) }
-<Sith> {
-    :feelingForce (true) ,
-    :attitute (!'good') ,
-    :laserSwordColor (!'blue') ,
-    :numberLaserSwords ('2'^^xsd:nonNegativeInteger) }
-\end{ex}
-
-Individual matching the 'Jedi' data shape:
-
-\begin{ex}
-:Joda 
-    :feelingForce (true) ;
-    :attitute ('good') ;
-    :laserSwordColor ('blue') ,
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger .
-\end{ex}
-
-Individual matching the 'Sith' data shape:
-
-\begin{ex}
-:DarthSidious
-    :feelingForce (true) ;
-    :attitute ('evil') ;
-    :laserSwordColor ('red') ,
-    :numberLaserSwords '2'^^xsd:nonNegativeInteger . 
-\end{ex}
-
-\subsection{Membership in Controlled Vocabularies}
-
-requirements:
-
-\begin{itemize}
-	\item R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES
-	\item R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES
-\end{itemize}
-
-constraint (DSP):
-
-\begin{ex}
-:bookDescriptionTemplate 
-    a dsp:DescriptionTemplate ;
-    dsp:resourceClass swrc:Book ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:property dcterms:subject ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass skos:Concept ; 
-            dsp:vocabularyEncodingScheme :BookSubjects, :BookTopics, :BookCategories ] ] .
-\end{ex}
-
-A DSP consists of \ms{dsp:DescriptionTemplate}s that put constraints on instances of a certain class (\ms{dsp:resourceClass}). 
-\ms{:bookDescriptionTemplate} describes resources of the type \ms{swrc:Book}.
-The constraints can either be constraints on the description itself, e.g.
-a minimum occurrence of instances of this class.
-Additionally, constraints on single properties can be defined within a \ms{dsp:StatementTemplate}.
-The \ms{dsp:NonLiteralStatementTemplate} restricts books to have \ms{dcterms:subject} (\ms{dsp:property}) relationships to RDF objects which are further described by the \ms{dsp:NonLiteralConstraint}.
-These RDF objects have to be of the class \ms{skos:Concept} (\ms{dsp:ValueClass}).
-Controlled vocabularies (like \ms{:BookSubjects}) are represented as \ms{skos:ConceptSchemes} in RDF and as \ms{dsp:VocabularyEncodingScheme}s in DSP.
-\ms{dsp:VocabularyEncodingScheme} points to a list of controlled vocabularies the \ms{skos:Concept} resources must be members of.
-The controlled vocabulary members (\ms{skos:Concept}s) are related to the controlled vocabulary (\ms{skos:ConceptScheme}) via the object properties \ms{skos:inScheme} and \ms{dcam:memberOf}.
-
-valid data (DSP):
-
-\begin{ex}
-:ArtficialIntelligence
-    a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
-    a skos:Concept ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
-    a skos:ConceptScheme .
-\end{ex}
-
-invalid data (DSP):
-
-\begin{ex}
-:ArtficialIntelligence
-    a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
-    a skos:Concept ;
-    dcam:memberOf :BooksAboutBirds ;
-    skos:inScheme :BooksAboutBirds ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
-    a skos:ConceptScheme .
-\end{ex}
-
-The related subject (\ms{:ComputerScience}) is a member of a controlled vocabulary (\ms{:BooksAboutBirds}) 
-which is not part of the list of allowed controlled vocabularies.
-
-\subsection{Pattern Matching}
-
-requirements:
-
-\begin{itemize}
-	\item R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS
-  \item R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS
-  \item R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES
-  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-  \item R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS
-\end{itemize}
-
-\subsubsection{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}
-
-Covering approaches:
-
-DQTP (MATCH Pattern), OWL 2 DL, RS, ShEx, SPARQL, SPIN
-
-constraints (OWL 2 DL) [description logics abstract syntax]:
-
-\begin{ex}
-
-\end{ex}
-
-constraints (OWL 2 DL) [functional-style syntax]:
-
-\begin{ex}
-Declaration( Datatype( :SSN ) ) 
-DatatypeDefinition( 
-    :SSN
-    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
-DataPropertyRange( :hasSSN :SSN ) 
-\end{ex}
-
-constraints (OWL 2 DL) [turtle syntax]:
-
-\begin{ex}
-:SSN 
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:string ;
-        owl:withRestrictions ( 
-            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
-\end{ex}
-
-\begin{itemize}
-	\item OWL 2 construct 'DatatypeRestriction' not allowed for OWL 2 QL
-\end{itemize}
-
-A social security number is a string that matches the given regular expression. 
-The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
-The first axiom explicitly declares :SSN to be a datatype. 
-The datatype :SSN can be used just like any other datatype; 
-for example, it is used in the third axiom to define the range of the :hasSSN property.
-
-valid data (OWL 2 DL):
-
-\begin{ex}
-:IimBernersLee
-    :hasSSN "123-45-6789"^^:SSN .
-\end{ex}
-
-invalid data (OWL 2 DL):
-
-\begin{ex}
-:IimBernersLee
-    :hasSSN "123456789"^^:SSN .
-\end{ex}
-
-\subsubsection{R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS}
-
-Covering approaches: DQTP (MATCH Pattern), OWL 2 DL, SPARQL, SPIN
-
-constraints (DQTP):
-
-MATCH Pattern \cite{Kontokostas2014}
-
-Application logic or real world constraints may put restrictions on the form of a literal value.
-P1 is the property we need to check against REGEX and
-NOP can be a not operator (!) or empty.
-
-\begin{ex}
-SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
-    FILTER ( %%NOP%% regex(str(?value), %%REGEX%) ) }
-\end{ex}
-
-example test bindings (DQTP):
-
-\begin{ex}
-1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
-2. dbo:postCode format is different ‘!’ from 'ˆ[0-9]{5}$'
-3. foaf:phone contains any letters ('[A-Za-z]')
-\end{ex}
-
-test binding (DQTP):
-
-\begin{ex}
-dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
-
-P1 => dbo:isbn
-NOP => !
-REGEX => 'ˆ([iIsSbBnN 0-9-])*$'
-\end{ex}
-
-valid data (DQTP):
-
-\begin{ex}
-:FoundationsOfSWTechnologies
-    dbo:isbn 'ISBN-13 978-1420090505' .
-\end{ex}
-
-invalid data (DQTP):
-
-\begin{ex}
-:HandbookOfSWTechnologies
-    dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
-\end{ex}
-
-\subsection{Calculations on and Comparisons of RDF Literals}
-
-requirements:
-
-\begin{itemize}
-	\item R-41-STATISTICAL-COMPUTATIONS
-	\item R-42-COMPUTATIONS-BASED-ON-DATATYPE
-	\item R-43-COMPARISONS-BASED-ON-DATATYPE
-	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
-\end{itemize}
-
-\subsubsection{R-41-STATISTICAL-COMPUTATIONS}
-
-\begin{itemize}
-  \item examples: average, mean, sum
-	\item covering approaches: SPARQL, SPIN
-\end{itemize}
-
-\subsubsection{R-42-COMPUTATIONS-BASED-ON-DATATYPE}
-
-\begin{itemize}
-	\item covering approaches: -
-\end{itemize}
-
-\subsubsection{R-43-COMPARISONS-BASED-ON-DATATYPE}
-
-\begin{itemize}
-	\item covering approaches: DQTP, ShEx, SPARQL, SPIN
-\end{itemize}
-
-constraints (DQTP):
-
-COMP Pattern \cite{Kontokostas2014}
-
-Depending on the property semantics,
-there are cases where two different literal values must have
-a specific ordering with respect to an operator. 
-P1 and P2 are the datatype properties we need to compare and 
-OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=).
-
-\begin{ex}
-SELECT ?s WHERE { 
-    ?s %%P1%% ?v1 .
-    ?s %%P2%% ?v2 .
-    FILTER ( ?v1 %%OP%% ?v2 ) }
-\end{ex}
-
-example bindings (DQTP):
-
-\begin{ex}
-1. dbo:deathDate before ‘<’ dbo:birthDate
-2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
-3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
-\end{ex}
-
-test binding (DQTP):
-
-dbo:deathDate before ‘\textless’ dbo:birthDate
-
-\begin{ex}
-P1 => dbo:deathDate
-P2 => dbo:birthDate
-OP => <
-\end{ex}
-
-valid data:
-
-\begin{ex}
-:AlbertEinstein
-    dbo:birthDate '1879-03-14'^^xsd:date ;
-    dbo:deathDate '1955-04-18'^^xsd:date .
-\end{ex}
-
-invalid data:
-
-\begin{ex}
-:NeilArmstrong
-    dbo:birthDate '2012-08-25'^^xsd:date ;
-    dbo:deathDate '1930-08-05'^^xsd:date .
-\end{ex}
-
-\subsubsection{R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS}
-
-\begin{itemize}
-	\item covering approaches: SPARQL, SPIN
-\end{itemize}
-
-\subsection{Constraining Facets on RDF Literals}
-
-XSD constraining facets: \url{http://www.w3.org/TR/2001/REC-xmlschema-2-20010502/#rf-facets}
-
-requirements:
-
-\begin{itemize}
-	\item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
-	\item R-46-CONSTRAINING-FACETS
-	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
-	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
-\end{itemize}
-
-\subsubsection{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}
-
-\begin{itemize}
-	\item see 'Pattern Matching'
-\end{itemize}
-
-\subsubsection{R-45-RANGES-OF-RDF-LITERAL-VALUES}
-
-constraints (OWL 2 DL) [description logics abstract syntax]:
-
-\begin{ex}
-ToDO
-\end{ex}
-
-constraints (OWL 2 DL) [functional-style syntax]:
-
-\begin{ex}
-Declaration( Datatype( :NumberPlayersPerWorldCupTeam ) ) 
-DatatypeDefinition( 
-    :NumberPlayersPerWorldCupTeam
-    DatatypeRestriction( 
-        xsd:nonNegativeInteger 
-        xsd:minInclusive "1"^^xsd:nonNegativeInteger 
-        xsd:maxInclusive "23"^^xsd:nonNegativeInteger ) )     
-DataPropertyRange( :position :NumberPlayersPerWorldCupTeam ) 
-\end{ex}
-
-constraints (OWL 2 DL) [turtle syntax]:
-
-\begin{ex}
-:NumberPlayersPerWorldCupTeam
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:nonNegativeInteger ;
-        owl:withRestrictions ( 
-            [ xsd:minInclusive "1"^^xsd:nonNegativeInteger ]
-            [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
-\end{ex}
-
-The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most.
-
-valid data (OWL 2 DL):
-
-\begin{ex}
-:MarioGoetze
-    :position "19"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-invalida data (OWL 2 DL):
-
-\begin{ex}
-:MarioGoetze
-    :position "99"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\subsection{Language of RDF Literals}
-
-requirements:
-
-\begin{itemize}
-	\item R-47-LANGUAGE-TAG-MATCHING
-  \item R-48-MISSING-LANGUAGE-TAGS
-	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
-\end{itemize}
-
-\subsubsection{R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}
-
-constraints (DQTP):
-
-ONELANGPattern \cite{Kontokostas2014}
-
-A literal value should contain at most
-1 literal for a language. P1 is the property containing the
-literal and V1 is the language we want to check.
-
-\begin{ex}
-SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
-    BIND ( lang(?c) AS ?l )
-    FILTER (isLiteral (?c) && lang(?c) = %%V1%%)}
-GROUP BY ?s HAVING COUNT (?l) > 1
-\end{ex}
-
-test binding (DQTP):
-
-a single English (“en”) foaf:name
-
-\begin{ex}
-P1 => foaf:name
-V1 => en
-\end{ex}
-
-valid data (DQTP):
-
-\begin{ex}
-:LeiaSkywalker
-    foaf:name 'Leia Skywalker'@en .
-\end{ex}
-
-invalid data (DQTP):
-
-\begin{ex}
-:LeiaSkywalker
-    foaf:name 'Leia Skywalker'@en ;
-    foaf:name 'Leia'@en .
-\end{ex}
-
-\subsection{Property Occurrences}
-
-requirements:
-
-\begin{itemize}
-	\item R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
-	\item R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
-	\item R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE
-\end{itemize}
-
-\subsubsection{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS}
-
-\begin{itemize}
-	\item instances of specific class must not have some object property
-  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
-	\item covering approaches: ShEx, SPIN
-\end{itemize}
-
-constraint (ShEx):
-
-A matching triple has any predicate except those excluded by the '!' operator.
-
-\begin{ex}
-<FeelingForce> {
-    :feelingForce (true) ,
-    :attitute xsd:string }
-<JediMentor> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-    :mentorOf @<JediStudent> ,
-   !:studentOf @<JediMentor> }
-<JediStudent> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-   !:mentorOf @<JediStudent> ,
-    :studentOf @<JediMentor> }
-\end{ex}
-
-individuals matching 'FeelingForce' and 'JediMentor' data shapes:
-
-\begin{ex}
-:Obi-Wan 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :mentorOf :Anakin .
-\end{ex}
-
-individuals matching 'FeelingForce' and 'JediStudent' data shapes:
-
-\begin{ex}
-:Anakin 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :studentOf :Obi-Wan .
-\end{ex}
-
-\subsubsection{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}
-
-\begin{itemize}
-	\item analogous to R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
-	\item covering approaches: ShEx, SPIN
-\end{itemize}
-
-\subsection{Property Groups}
-
-requirements:
-
-\begin{itemize}
-	\item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-	\item R-66-PROPERTY-GROUPS
-\end{itemize}
-
-\subsection{RDF-Specific Validation}
-
-requirements:
-
-\begin{itemize}
-	\item R-120-HANDLE-RDF-COLLECTIONS
-\end{itemize}
-
-\subsubsection{R-120-HANDLE-RDF-COLLECTIONS}
-
-examples:
-
-\begin{itemize}
-	\item size of collection
-	\item first / last element of list must be a specific RDF literal
-	\item compare elements of collection
-	\item are collections identical?
-	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
-	\item 2. list element equals ''
-	\item Does the list have more than 10 elements?
-\end{itemize}
-
-constraint (SPIN):
-
-retrieves the 2. item from the list (2. student of Jedi mentor Jinn)
-
-function call (SPIN):
-
-\begin{ex}
-BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
-\end{ex}
-
-function (SPIN):
-
-\begin{ex}
-:getListItem
-    a spin:Function ; rdfs:subClassOf spin:Functions ;
-    spin:constraint [
-        rdf:type spl:Argument ;
-        spl:predicate sp:arg1 ;
-        spl:valueType rdf:List ;
-        rdfs:comment "list" ; ] ;
-    spin:constraint [
-        rdf:type spl:Argument ;
-        spl:predicate sp:arg2 ;
-        spl:valueType xsd:nonNegativeInteger ;
-        rdfs:comment "item position (starting with 0)" ; ] ;
-    spin:body [
-        a sp:SELECT ;
-        sp:text """
-            SELECT ?item
-            WHERE {
-                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
-    spin:returnType rdfs:Resource .
-\end{ex}
-
-data:
-
-\begin{ex}
-:Jinn :students 
-     ( :Xanatos :Kenobi ) . 
-\end{ex}
-
-result:
-
-\begin{ex}
-:Kenobi
-\end{ex}
-
-\subsection{RDF Shapes}
-
-requirements:
-
-\begin{itemize}
-	\item R-125-RDF-SHAPE-CHECKING
-\end{itemize}
-
-\subsection{RDF Validation Results}
-
-requirements:
-
-\begin{itemize}
-	\item R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS
-	\item R-151-USEFUL-MESSAGE-VALIDATION-RESULTS
-	\item R-152-FIND-NOT-VALIDATED-TRIPLES
-	\item R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS
-	\item R-154-HANDLE-CONSTRAINT-VIOLATIONS
-	\item R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA
-	\item R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS
-	\item R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS
-	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
-	\item R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS
-\end{itemize}
-
-\subsection{Requirements Covered by OWL 2 DL But Not by OWL 2 QL}
-
-\section{Related Work}
-
-\section{Evaluation}
-
-\subsection{Evaluation Using Practical Data Set}
-
-\subsection{RDF Validation Requirements Covered by OWL 2 QL}
-
-Table~\ref{tab:RequirementsCoveredOWL2QL}
-
-\begin{table}
-\caption{RDF Validation Requirements Covered by OWL 2 QL}
-\label{tab:RequirementsCoveredOWL2QL}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-& R-1-UNIQUENESS-OF-URIS \\
-& R-2-UNIQUE-INSTANCES \\
-& R-3-EQUIVALENT-CLASSES (EquivalentClasses) \\
-& R-4-EQUIVALENT-OBJECT-PROPERTIES (EquivalentObjectProperties) \\
-& R-5-EQUIVALENT-DATA-PROPERTIES (EquivalentDataProperties) \\
-& R-7-DISJOINT-CLASSES (DisjointClasses) \\
-& R-9-DISJOINT-OBJECT-PROPERTIES (DisjointObjectProperties) \\
-& R-10-DISJOINT-DATA-PROPERTIES (DisjointDataProperties) \\
-& R-14-DISJOINT-INDIVIDUALS (DifferentIndividuals) \\
-& R-25-OBJECT-PROPERTY-DOMAIN (ObjectPropertyDomain) \\
-& R-26-DATA-PROPERTY-DOMAIN (DataPropertyDomain) \\
-& R-27-CLASS-SPECIFIC-VALIDATION \\
-& R-28-OBJECT-PROPERTY-RANGE (ObjectPropertyRange) \\
-& R-35-DATA-PROPERTY-RANGE (DataPropertyRange) \\
-& R-54-SUB-OBJECT-PROPERTIES (SubObjectPropertyOf) \\
-& R-56-INVERSE-OBJECT-PROPERTIES (ObjectInverseOf) \\
-& R-59-REFLEXIVE-OBJECT-PROPERTIES (ReflexiveObjectProperty) \\
-& R-60-IRREFLEXIVE-OBJECT-PROPERTIES (IrreflexiveObjectProperty) \\
-& R-61-SYMMETRIC-OBJECT-PROPERTIES (SymmetricObjectProperty) \\
-& R-62-ASYMMETRIC-OBJECT-PROPERTIES (AsymmetricObjectProperty) \\
-& R-64-SUB-DATA-PROPERTIES (SubDataPropertyOf) \\
-& R-93-DIFFERENCE-BETWEEN-CONSTRAINTS-ON-OBJECT-AND-DATA-PROPERTIES \\
-& R-94-POSITIVE-OBJECT-PROPERTY-ASSERTIONS (ObjectPropertyAssertion) \\
-& R-95-POSITIVE-DATA-PROPERTY-ASSERTIONS (DataPropertyAssertion) \\
-& R-99-STABLE-IDENTIFICATION-OF-CONSTRAINTS \\
-& R-100-SUBSUMPTION (SubClassOf) \\
-& R-101-DECLARATIVE-CONSTRAINT-LANGUAGE \\
-& R-102-INTUITIVE-CONSTRAINT-LANGUAGE \\
-& R-103-HIGH-LEVEL-CONSTRAINT-LANGUAGE \\
-& R-104-CONSTRAINT-LANGUAGE-HAVING-IMPLEMENTATION-LANGUAGE \\
-& R-105-CONSTRAINT-LANGUAGE-TRANSLATABLE-TO-IMPLEMENTATION-LANGUAGE \\
-& R-107-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-UML \\
-& R-108-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-XML-SCHEMA \\
-& R-109-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-OCL \\
-& R-110-TRANSFORMATIONS-BETWEEN-CONSTRAINT-LANGUAGE-AND-SPARQL \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Covered by OWL 2 QL}
-\label{tab:RequirementsCoveredOWL2QL}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-& R-111-BASIC-USE-CASES-COVERED-BY-CONSTRAINT-LANGUAGE \\
-& R-113-INTERACTION-OF-VALIDATION-WITH-REASONING \\
-& R-115-CLOSED-WORLD-ASSUMPTION-CWA \\
-& R-116-UNIQUE-NAME-ASSUMPTION-UNA \\
-& R-117-CONTEXT-SENSITIVE-CONSTRAINTS \\
-& R-118-NAMESPACE-SENSITIVE-CONSTRAINTS \\
-& R-122-TRADE-OFF-BETWEEN-DIMENSIONS-EXPRESSIVITY-COMPLEXITY-PREDICTABILITY \\
-& R-124-DESCRIBE-DATA \\
-& R-126-CUSTOMIZABLE-VALIDATION-PROCESS \\
-& R-128-HUMAN-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
-& R-129-MACHINE-UNDERSTANDABLE-CONCRETE-SYNTAXES-FORMULATION-CONSTRAINTS \\
-& R-130-CONCISE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
-& R-131-OWL-AS-CONCRETE-SYNTAX-FORMULATING-CONSTRAINTS \\
-& R-132-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-CONSTRAINTS \\
-& R-133-MULTIPLE-CONCRETE-SYNTAXES-FORMULATING-DATA \\
-& R-136-MODULARITY-OF-CONSTRAINT-DEFINITIONS \\
-& R-137-LEVERAGE-ON-EXISTING-TECHNOLOGIES \\
-& R-138-CONSTRAINT-LANGUAGE-COMPATIBLE-WITH-SPARQL \\
-& R-139-CONSTRAINT-LANGUAGE-DRIVES-USER-INTERFACE-FORM-GENERATION-AND-PRESENTATION \\
-& R-140-SEPARATE-ONTOLOGIES-FROM-VALIDATION-SCHEMAS \\
-& R-143-CONDITIONAL-TYPED-VALIDATION \\
-& R-147-DISTRIBUTION-OF-CONSTRAINT-SCHEMAS \\
-& R-148-DISTRIBUTED-VALIDATION-IN-COLLABORATIVE-ENVIRONMENTS \\
-& R-149-MANAGEMENT-OF-CONSTRAINT-SCHEMA-EVOLUTION \\
-& R-160-OPEN-SOURCE-CONSTRAINT-VALIDATION \\
-& R-161-ACCEPTABLE-PERFORMANCE-OF-VALIDATION-ALGORITHM \\
-& R-162-SPECIFICATION-PUBLICLY-AVAILABLE \\
-& R-163-IMPLEMENTATION-EXISTS \\
-& R-164-IMPLEMENTATION-PUBLICLY-AVAILABLE \\
-& R-165-EXECUTABLE-DEMOS-EXAMPLES-USE-CASES \\
-& R-168-PERFORM-BIG-DATASETS \\
-& R-169-RDF-REPRESENTATION-OF-CONSTRAINT-LANGUAGE \\
-& R-173-SEPARATE-CONSTRAINTS-FROM-VOCABULARIES-AND-ONTOLOGIES \\
-& R-174-REUSE-CONSTRAINTS \\
-& R-175-DISCOVER-CONSTRAINTS \\
-& R-177-DEFINE-SEMANTICS-FOR-CONSTRAINTS \\
-& R-178-ASSOCIATE-CONSTRAINTS-WITH-VOCABULARIES \\
-& R-182-USE-KNOWN-CONCRETE-SYNTAX \\
-& R-184-COMPACT-CONCRETE-SYNTAX \\
-& R-187-DEFINE-SEMANTICS-OF-CONSTRAINTS-IN-TERMS-OF-SPARQL \\
-& R-190-SPECIFY-EXPECTED-BEHAVIOR-UNDER-ALL-POSSIBLE-ENTAILMENT-REGIMES \\
-& R-192-DEFINE-ANNOTATIONS-FOR-CONSTRAINTS \\
-& R-195-CONSTRAINT-LANGUAGE-EASY-TO-CONSUME-BY-TOOLS \\
-& R-197-ATTACH-CONSTRAINTS-TO-CLASSES \\
-& R-198-RDF-VALIDATION-AFTER-INFERENCING \\
-& R-199-RDF-VALIDATION-MUST-COMPILE-DOWN-TO-SPARQL \\
-\hr
-\end{tabular}
-\end{table}
-
-\subsection{RDF Validation Requirements Not Covered by OWL 2 QL}
-
-Table~\ref{tab:RequirementsNotCoveredOWL2QL-1}
-Table~\ref{tab:RequirementsNotCoveredOWL2QL-2}
-Table~\ref{tab:RequirementsNotCoveredOWL2QL-3}
-
-%\medskip% adds some space before the table
-%\begin{adjustwidth}{-1in}{-1in}% adjust the L and R margins by 1 inch
-  %\begin{tabular}{ll}
-    %\toprule
-    %Requirements & Covering Constraint Languages \\
-    %\midrule
-%R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-%R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-%R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-%R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-%R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-%R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-%R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-%R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (ObjectUnionOf) & OWL 2 DL \\
-%R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-%R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-%R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-%R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-%R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-%R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-%R-24-PROVENANCE-CONSTRAINTS & \\
-%R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-%R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-%R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-%R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-%R-33-NEGATIVE-OBJECT-CONSTRAINTS \\
-%R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-%R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-%R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-%R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-%R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-%R-44-PATTERN-MATCHING-ON-RDF-LITERALS & ShEx, RS, SPIN \\
-%R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-%R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-%R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-%R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-%R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-%R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-%R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-%R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-%R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-%R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-%R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-%R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-%R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-%R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-%R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-%R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-%R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-%R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-%R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-%R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-%R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-%R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-%R-71-CONDITIONAL-PROPERTIES \\
-%R-72-RECOMMENDED-PROPERTIES \\
-%R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-%R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-%R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, SPIN \\
-%R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-    %\bottomrule
-  %\end{tabular}
-%\end{adjustwidth}
-%\medskip% adds some space after the table
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
-\label{tab:RequirementsNotCoveredOWL2QL-1}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements & Covering Constraint Languages \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-R-24-PROVENANCE-CONSTRAINTS & \\
-R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
-R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
-R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-71-CONDITIONAL-PROPERTIES \\
-R-72-RECOMMENDED-PROPERTIES \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
-\label{tab:RequirementsNotCoveredOWL2QL-2}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements & Covering Constraint Languages \\
-\hr
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL}
-\label{tab:RequirementsNotCoveredOWL2QL-3}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements & Covering Constraint Languages \\
-\hr
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
-R-98-CHECK-VALIDITY-OF-URIS & \\
-R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
-R-112-EXTENSIBLE-CONSTRAINTS & \\
-R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
-R-119-VALIDATION-ON-NAMED-GRAPHS & \\
-R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
-R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
-R-123-STATE & \\
-R-125-RDF-SHAPE-CHECKING & ShEx \\
-R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
-R-134-SPECIFY-USAGE-OF-TERMS & \\
-R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
-R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
-R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
-R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
-R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
-R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
-R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
-R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
-R-166-RDF-STREAMING-VALIDATION & \\
-R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
-R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
-R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
-R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
-R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
-R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
-R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
-R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
-R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
-R-185-FEDERALIZED-RDF-VALIDATION & \\
-R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
-R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
-R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
-R-191-SHAPES-RELATED-TO-TYPES & \\
-R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
-R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
-\label{tab:RequirementsCoveredOWL2DL}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification (1. level) & Requirements \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS (DatatypeDefinition, DatatypeRestriction) \\
-R-46-CONSTRAINING-FACETS (DatatypeDefinition, DatatypeRestriction) \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) \\
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) \\
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS (DatatypeDefinition, DatatypeRestriction) \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
-\label{tab:RequirementsCoveredShEx}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-R-24-PROVENANCE-CONSTRAINTS & \\
-R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
-R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
-R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-71-CONDITIONAL-PROPERTIES \\
-R-72-RECOMMENDED-PROPERTIES \\
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
-R-98-CHECK-VALIDITY-OF-URIS & \\
-R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
-R-112-EXTENSIBLE-CONSTRAINTS & \\
-R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
-R-119-VALIDATION-ON-NAMED-GRAPHS & \\
-R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
-R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
-R-123-STATE & \\
-R-125-RDF-SHAPE-CHECKING & ShEx \\
-R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
-R-134-SPECIFY-USAGE-OF-TERMS & \\
-R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
-R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
-R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
-R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
-R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
-R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
-R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
-R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
-R-166-RDF-STREAMING-VALIDATION & \\
-R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
-R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
-R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
-R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
-R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
-R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
-R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
-R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
-R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
-R-185-FEDERALIZED-RDF-VALIDATION & \\
-R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
-R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
-R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
-R-191-SHAPES-RELATED-TO-TYPES & \\
-R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
-R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
-\label{tab:RequirementsCoveredShEx}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-R-24-PROVENANCE-CONSTRAINTS & \\
-R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
-R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
-R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-71-CONDITIONAL-PROPERTIES \\
-R-72-RECOMMENDED-PROPERTIES \\
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
-R-98-CHECK-VALIDITY-OF-URIS & \\
-R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
-R-112-EXTENSIBLE-CONSTRAINTS & \\
-R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
-R-119-VALIDATION-ON-NAMED-GRAPHS & \\
-R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
-R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
-R-123-STATE & \\
-R-125-RDF-SHAPE-CHECKING & ShEx \\
-R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
-R-134-SPECIFY-USAGE-OF-TERMS & \\
-R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
-R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
-R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
-R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
-R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
-R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
-R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
-R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
-R-166-RDF-STREAMING-VALIDATION & \\
-R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
-R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
-R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
-R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
-R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
-R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
-R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
-R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
-R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
-R-185-FEDERALIZED-RDF-VALIDATION & \\
-R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
-R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
-R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
-R-191-SHAPES-RELATED-TO-TYPES & \\
-R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
-R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
-\hr
-\end{tabular}
-\end{table}
-
-\begin{table}
-\caption{RDF Validation Requirements Only Covered by SPIN and SPARQL}
-\label{tab:RequirementsCoveredSPIN}
-\centering
-\begin{tabular}{ll}
-\hr
-Requirements Classification & Requirements \\
-\hr
-R-6-EQUIVALENT-INDIVIDUALS (SameIndividual) & OWL 2 DL \\
-R-8-DISJOINT-UNION-OF-CLASS-EXPRESSIONS (DisjointUnion) & OWL 2 DL \\
-R-11-DISJOINT-DATA-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-12-DISJOINT-OBJECT-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC & ShEx \\
-R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS (ObjectIntersectionOf) & OWL 2 DL \\
-R-16-CONJUNCTION-OF-DATA-RANGES (DataIntersectionOf) & OWL 2 DL \\
-R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS (DisjointUnionOf) & OWL 2 DL \\
-R-18-DISJUNCTION-OF-DATA-RANGES (DataUnionOf) & OWL 2 DL \\
-R-19-NEGATION-OF-CLASS-EXPRESSIONS (ObjectComplementOf) & OWL 2 DL \\
-R-20-NEGATION-OF-DATA-RANGES (DataComplementOf) & OWL 2 DL \\
-R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS & SPIN \\
-R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS & SPIN, ShEx \\
-R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES & SPIN, ShEx \\
-R-24-PROVENANCE-CONSTRAINTS & \\
-R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS & SPIN, RS \\
-R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS (ObjectOneOf) & OWL 2 DL \\
-R-31-DEFAULT-VALUES-OF-RDF-OBJECTS & SPIN, BF, RS \\
-R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-33-NEGATIVE-OBJECT-CONSTRAINTS & ShEx, SPIN \\
-R-34-AVAILABLE-CLASS-DEFINITION & ShEx, SPIN \\
-R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS & ShEx, BF, SPIN \\
-R-37-ALLOWED-VALUES-FOR-RDF-LITERALS (DataOneOf) & OWL 2 DL \\
-R-38-DEFAULT-VALUES-OF-RDF-LITERALS & SPIN, BF, RS \\
-R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES & DSP, SPIN \\
-R-44-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, ShEx, RS, SPARQL, SPIN \\
-R-41-STATISTICAL-COMPUTATIONS & SPIN \\
-R-42-COMPUTATIONS-BASED-ON-DATATYPE & \\
-R-43-COMPARISONS-BASED-ON-DATATYPE & DQTP, ShEx, SPIN \\
-R-45-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-46-CONSTRAINING-FACETS & Stardog, SPIN \\
-R-47-LANGUAGE-TAG-MATCHING & SPIN \\
-R-48-MISSING-LANGUAGE-TAGS & SPIN \\
-R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG & DQTP, SPIN \\
-R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-51-HTML-HANDLING-OF-RDF-LITERALS & SPIN \\
-R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS & ShEx, SPIN \\
-R-55-OBJECT-PROPERTY-PATHS (SubObjectPropertyOf) & OWL 2 DL \\
-R-57-FUNCTIONAL-OBJECT-PROPERTIES (FunctionalObjectProperty) & OWL 2 DL \\
-R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES (InverseFunctionalObjectProperty) & OWL 2 DL \\
-R-63-TRANSITIVE-OBJECT-PROPERTIES (TransitiveObjectProperty) & OWL 2 DL \\
-R-65-FUNCTIONAL-DATA-PROPERTIES (FunctionalDataProperty) & OWL 2 DL \\
-R-66-PROPERTY-GROUPS & ShEx, SPIN \\
-R-67-CLASSIFY-PROPERTIES-ACCORDING-TO-OCCURRENCE & \\
-R-68-REQUIRED-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-69-OPTIONAL-PROPERTIES  (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-70-REPEATABLE-PROPERTIES (ObjectMinCardinality, DataMinCardinality) & OWL 2 DL \\
-R-71-CONDITIONAL-PROPERTIES \\
-R-72-RECOMMENDED-PROPERTIES \\
-R-74-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-75-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-76-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-77-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-78-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-79-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-80-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectExactCardinality) & OWL 2 DL \\
-R-81-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMinCardinality) & OWL 2 DL \\
-R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-OBJECT-PROPERTIES (ObjectMaxCardinality) & OWL 2 DL \\
-R-83-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataExactCardinality) & OWL 2 DL \\
-R-84-MINIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMinCardinality) & OWL 2 DL \\
-R-85-MAXIMUM-UNQUALIFIED-CARDINALITY-RESTRICTIONS-ON-DATA-PROPERTIES (DataMaxCardinality) & OWL 2 DL \\
-R-86-EXISTENTIAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectSomeValuesFrom) & OWL 2 DL \\
-R-87-UNIVERSAL-QUANTIFICATION-ON-OBJECT-PROPERTIES (ObjectAllValuesFrom) & OWL 2 DL \\
-R-88-INDIVIDUAL-VALUE-RESTRICTION-ON-OBJECT-PROPERTIES (ObjectHasValue) & OWL 2 DL \\
-R-89-SELF-RESTRICTION (ObjectHasSelf) & OWL 2 DL \\
-R-90-EXISTENTIAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataSomeValuesFrom) & OWL 2 DL \\
-R-91-UNIVERSAL-QUANTIFICATION-ON-DATA-PROPERTIES (DataAllValuesFrom) & OWL 2 DL \\
-R-92-LITERAL-VALUE-RESTRICTION (DataHasValue) & OWL 2 DL \\
-R-96-NEGATIVE-OBJECT-PROPERTY-ASSERTIONS (NegativeObjectPropertyAssertion) & OWL 2 DL \\
-R-97-NEGATIVE-DATA-PROPERTY-ASSERTIONS (NegativeDataPropertyAssertion) & OWL 2 DL \\
-R-98-CHECK-VALIDITY-OF-URIS & \\
-R-106-EXTENSIBLE-CONSTRAINT-LANGUAGE & \\
-R-112-EXTENSIBLE-CONSTRAINTS & \\
-R-114-PROVIDE-RDF-REST-SERVICES-FOR-RDF-VALIDATION & \\
-R-119-VALIDATION-ON-NAMED-GRAPHS & \\
-R-120-HANDLE-RDF-COLLECTIONS & ShEx, SPIN \\
-R-121-SPECIFY-ORDER-OF-RDF-RESOURCES & \\
-R-123-STATE & \\
-R-125-RDF-SHAPE-CHECKING & ShEx \\
-R-126-CUSTOMIZABLE-VALIDATION-PROCESS & \\
-R-134-SPECIFY-USAGE-OF-TERMS & \\
-R-135-CONSTRAINT-LEVELS & \\
-R-141-NEGATIVE-PATTERN-MATCHING-ON-RDF-LITERALS & DQTP, OWL 2 DL, SPARQL, SPIN \\
-R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES & DQTP, SPIN \\
-R-146-CONSTRAINT-VALIDATION-OF-RDF-INPUT-WITH-RESPECT-TO-EXISTING-RDF & \\
-R-150-RDF-REPRESENTATION-OF-VALIDATION-RESULTS & SPIN, DQTP \\
-R-151-USEFUL-MESSAGE-VALIDATION-RESULTS & SPIN, DQTP, ShEx, Pellet \\
-R-152-FIND-NOT-VALIDATED-TRIPLES & ShEx \\
-R-153-RDF-REPRESENTATION-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-154-HANDLE-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-155-GUIDANCE-HOW-TO-BECOME-VALID-DATA & ShEx, SPIN \\
-R-156-REFERENCES-TO-TRIPLES-CAUSING-THE-CONSTRAINT-VIOLATIONS & SPIN \\
-R-157-REFERENCES-TO-VALIDATION-RULES-CAUSING-CONSTRAINT-VIOLATIONS & ShEx, SPIN \\
-R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS & SPIN \\
-R-159-EXPLAIN-REASONS-OF-CONSTRAINT-VIOLATIONS & SPIN, ShEx, Stardog, Pellet \\
-R-166-RDF-STREAMING-VALIDATION & \\
-R-167-VALIDATE-RDF-IN-AN-HTML-DOCUMENT-CONSTAINING-RDFA-MARKUP & \\
-R-170-VALIDATION-OF-SPARQL-ENDPOINTS & \\
-R-171-VALIDATION-OF-URIS-BY-DEREFERENCING & \\
-R-172-GENERATE-HUMAN-READABLE-DOCUMENTATION & \\
-R-176-PROVIDE-HIGH-LEVEL-VOCABULARY-FOR-THE-MOST-COMMON-TYPES-OF-CONSTRAINTS & \\
-R-179-ASSOCIATE-CONSTRAINTS-WITH-RDF-DOCUMENTS & \\
-R-180-ASSOCIATE-CONSTRAINTS-WITH-RDF-DATASETS & \\
-R-181-ASSOCIATE-CONSTRAINTS-WITH-RDF-REST-APIS & \\
-R-183-CONSTRAINTS-ABOUT-CONSTRAINTS & \\
-R-185-FEDERALIZED-RDF-VALIDATION & \\
-R-186-EXTEND-EXPRESSIVITY-WITH-SPARQL & \\
-R-188-EXPRESSIVITY-OF-CONSTRAINT-LANGUAGE-EQUIVALENT-TO-SPARQL & \\
-R-189-ADD-ANNOTATIONS-TO-CONSTRAINT-VIOLATION-OBJECTS & \\
-R-191-SHAPES-RELATED-TO-TYPES & \\
-R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS & \\
-R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS & SPARQL, SPIN \\
-R-200-NEGATIVE-LITERAL-CONSTRAINTS & ShEx, SPARQL, SPIN \\
-\hr
-\end{tabular}
-\end{table}
-
-\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by OWL 2 DL}
-
-\begin{itemize}
-	\item OWL 2 DL as an instantiation of constraint languages which are high-level, human-friendly, and very expressive 
-\end{itemize}
-
-Table~\ref{tab:RequirementsCoveredOWL2DL}
-
-\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
-
-\begin{itemize}
-	\item ShEx as an instantiation of constraint languages which are high-level, human-friendly, intuitive, concise, and less expressive 
-\end{itemize}
-
-\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by ShEx}
-
-Table~\ref{tab:RequirementsCoveredShEx}
-
-\subsubsection{RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN and SPARQL}
-
-\begin{itemize}
-	\item SPIN as an instantiation of constraint languages which are low-level and the most expressive 
-\end{itemize}
-
-\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by SPIN and SPARQL}
-\tb{ToDo: RDF Validation Requirements Not Covered by OWL 2 QL But by DQTP}
-
-Table~\ref{tab:RequirementsCoveredSPIN}
-
-\section{Conclusion and Future Work}
-
-\section{Appendix}
-
-\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
-
-\textbf{Subclass Expressions}
-
-\begin{ex}
-subClassExpression :=
-    Class |
-    subObjectSomeValuesFrom | DataSomeValuesFrom
-subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
-\end{ex}
-
-\textbf{Superclass Expressions}
-
-\begin{ex}
-superClassExpression :=
-    Class |
-    superObjectIntersectionOf | superObjectComplementOf |
-    superObjectSomeValuesFrom | DataSomeValuesFrom
-\end{ex}
-
-\subsection{Supported Constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item subclass axioms (SubClassOf)
-  \item class expression equivalence (EquivalentClasses)
-  \item class expression disjointness (DisjointClasses)
-  \item inverse object properties (InverseObjectProperties)
-  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
-  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
-  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
-  \item property range (ObjectPropertyRange and DataPropertyRange)
-  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
-  \item symmetric properties (SymmetricObjectProperty)
-  \item reflexive properties (ReflexiveObjectProperty)
-  \item irreflexive properties (IrreflexiveObjectProperty)
-  \item asymmetric properties (AsymmetricObjectProperty)
-  \item assertions: DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion
-\end{itemize}
-
-\subsection{Not Supported Constructs in OWL 2 QL}
-
-\begin{itemize}
-	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
-  \item self-restriction (ObjectHasSelf)
-  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
-  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
-  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
-  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
-  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
-  \item property inclusions (SubObjectPropertyOf) involving property chains
-  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
-  \item transitive properties (TransitiveObjectProperty)
-  \item keys (HasKey)
-  \item individual equality assertions and negative property assertions (SameIndividual, NegativeObjectPropertyAssertion, NegativeDataPropertyAssertion)
-\end{itemize}
+And if there is a new constraint not covered by any constraint language you can just define the SPIN mapping for this constraint.
 

### 2014-10-07 paper/paper1.tex
DC 2014 tutorial
tutorial DC 2014
ideas of Kai

@@
 \section{Ideas}
+
+Ideas of Kai:
+RDF validation using OWL 2 QL reasoning by SPARQL query expansion
+validation with mappings to SPARQL
+if using OWL 2 DL as constraint language or using constraints equivalent to OWL 2 QL you can use reasoning 
+reasoning can also be executed SPARQL query expansion.
+reasoning not executing using reasoner
+limitations of this approach
+expressivity of SPARQL? (Erman) what can not be done with SPARQL?
 
@@
             [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
+:hasSSN rdfs:range :SSN .
 \end{ex}
@@
 \begin{ex}
-:IimBernersLee
+:TimBernersLee
     :hasSSN "123-45-6789"^^:SSN .
@@
 \begin{ex}
-:IimBernersLee
+:TimBernersLee
     :hasSSN "123456789"^^:SSN .
@@
 \subsubsection{R-45-RANGES-OF-RDF-LITERAL-VALUES}
+
+covering approaches: DQTP, OWL 2 DL, SPARQL, SPIN
 
@@
             [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
+:position rdfs:range :NumberPlayersPerWorldCupTeam .
 \end{ex}
@@
   \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
-	\item covering approaches: ShEx, SPIN
+	\item covering approaches: ShEx, SPIN, SPARQL
 \end{itemize}

### 2014-10-07 paper/paper3.tex
ideas of Kai

@@
 
+\section{XX}
+
+ontology describing constraint languages
+interoperability between constraint languages
+express constraint in CL A and translate constraint in CL B
+provide SPARQL validation (SPIN mapping) for each general C
+
+\section{constraint language ontology}
+
+\section{examples}
+
+\subsection{min cardinality}
+
+OWL 2:
+\begin{ex}
+foaf:Person
+    a owl:Restriction ;
+		owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
+		owl:onProperty :hasName ;
+		owl:onClass xsd:string .
+\end{ex}
+
+general constraint: min cardinality
+constraint (OWL2): data min cardinality
+
+translation to SPARQL:
+\begin{ex}
+
+\end{ex}
+
+\subsection{object property range}
+
+DSCL constraint (OWL 2):
+\begin{ex}
+:hasDog rdfs:range :Dog . 
+\end{ex}
+
+DSCL constraint (DSP):
+\begin{ex}
+:hasDogRange
+        a dsp:DescriptionTemplate ; 
+        dsp:resourceClass owl:Thing ; 
+        dsp:statementTemplate [
+            a dsp:NonLiteralStatementTemplate ;
+            dsp:property :hasDog ; 
+            dsp:nonLiteralConstraint [ 
+                a dsp:NonLiteralConstraint ;
+                dsp:valueClass :Dog ] ] .
+\end{ex}
+
+general constraint:
+\begin{ex}
+clo:objectPropertRange
+    a clo:GeneralConstraint ;
+		clo:requirement clo:R-28-OBJECT-PROPERTY-RANGE ;
+		clo:DSCLConstraints ( clo:objectPropertRange_OWL2 clo:objectPropertRange_DSP ) ;
+		clo:objectProperty :hasDog ;
+		clo:range ( :Dog ) ;
+\end{ex}
+
+valid data:
+\begin{ex}
+:Peter 
+    :hasDog :Brian .
+:Brian 
+    a :Dog ;     
+    a owl:Thing . 
+\end{ex}
+
+invalid data:
+\begin{ex}
+:Peter 
+    :hasDog :Brian .
+:Brian 
+#   a :Dog ; # commented --> constraint violation
+    a owl:Thing . 
+\end{ex}
+
+general constraint: object property range
+constraint (OWL2): object property range
+
+general C is translated to SPARQL for automatic validation
+
+for each DSCL constraint you have to define the binding to the general constraint.
+
+binding (DSCL constraint (OWL2) - general constraint):
+\begin{ex}
+# OWL 2 constraint
+# -----
+?OPE rdfs:range ?CE .
+
+clo:objectProperty => ?OPE
+clo:range => ?CE 
+\end{ex}
+
+binding (DSCL constraint (OWL2) - general constraint):
+\begin{ex}
+# DSP constraint
+# -----
+:hasDogRange
+        a dsp:DescriptionTemplate ; 
+        dsp:resourceClass owl:Thing ; 
+        dsp:statementTemplate [
+            a dsp:NonLiteralStatementTemplate ;
+            dsp:property :hasDog ; 
+            dsp:nonLiteralConstraint [ 
+                a dsp:NonLiteralConstraint ;
+                dsp:valueClass :Dog ] ] .
+
+# SPIN
+# -----
+?descriptionTemplate a dsp:DescriptionTemplate .
+?descriptionTemplate dsp:resourceClass ?resourceClass .
+?descriptionTemplate dsp:statementTemplate ?statementTemplate .
+?statementTemplate dsp:property ?property .
+?statementTemplate dsp:nonLiteralConstraint ?nonLiteralConstraint .
+?nonLiteralConstraint dsp:valueClass ?valueClass .				
+FILTER EXISTS { ?nonLiteralConstraint dsp:valueClass ?valueClass . }
+FILTER NOT EXISTS { ?object a ?valueClass . ?nonLiteralConstraint dsp:valueClass ?valueClass . }
+
+# binding (DSCL constraint (OWL2) - general constraint)
+# -----
+clo:objectProperty => ?OPE
+clo:range => ?CE 
+\end{ex}
+
+binding using SPIN
+
+SPARQL (validation of general constraint):
+\begin{ex}
+?x ?clo:objectProperty ?this .
+?this rdf:type owl:Thing . 
+FILTER NOT EXISTS { ?this a ?clo:range } .
+\end{ex}
+
+SPARQL (validation of DSCL constraint (OWL2)):
+\begin{ex}
+# constraint
+# -----
+?OPE rdfs:range ?CE .
+
+# data 
+# ----- 
+?x ?OPE ?this .
+?this rdf:type owl:Thing . 
+FILTER NOT EXISTS { ?this rdf:type ?CE } .
+\end{ex}
+
+SPARQL (validation of DSCL constraint (DSP)):
+\begin{ex}
+# data 
+# -----
+?this a ?resourceClass .
+?this ?property ?object .
+FILTER ( ?property != rdf:type ) .
+
+# constraint
+# -----
+?descriptionTemplate a dsp:DescriptionTemplate .
+?descriptionTemplate dsp:resourceClass ?resourceClass .
+?descriptionTemplate dsp:statementTemplate ?statementTemplate .
+?statementTemplate dsp:property ?property .
+?statementTemplate dsp:nonLiteralConstraint ?nonLiteralConstraint .
+?nonLiteralConstraint dsp:valueClass ?valueClass .				
+FILTER EXISTS { ?nonLiteralConstraint dsp:valueClass ?valueClass . }
+FILTER NOT EXISTS { ?object a ?valueClass . ?nonLiteralConstraint dsp:valueClass ?valueClass . }
+\end{ex}
+
+ontology design pattern.org
+constraint grammar
+constraint elements are the same
+DSP uses other design pattern / 
+constraint / constraint elements / constraint design patterns / constraint language
+define terminology
+related to requirements DB / relate requirements to constraints, constraint languages
+constraint element: e.g. min cardinality
+dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
+min car more powerful than req. propery
+why ontology? automatic translation from DSP to OWL 
+define general constraint language
+we do not invent a new constraint languages
+requirements in SPARQL umsetzten
+only one validation for each requirement
+constraints may be composed
+
 \bibliography{literatur}{}
